### 2013-05-22 paper.tex
Old paper

% This is "bach-ref-2009.tex" Updated january 29th 2010.
% This file should be compiled with "sig-alternate-fixed.cls" January 2010.
% It is based on the ACM style "sig-alternate.cls"
% -------------------------------------------------------------------------
% This example file demonstrates the use of the 'sig-alternate-fixed.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to the Twente Student Conference on IT. Both this file as the 
% document class file are based upon ACM documents.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line TSConIT
%       4) NO page numbers
%       5) NO headers and/or footers
%
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%

% refers to the cls file being used
\documentclass{sig-alternate-br}

\usepackage{graphicx}
\usepackage{rotating}

\begin{document}
%
% --- Author Metadata here --- DO NOT REMOVE OR CHANGE 
\conferenceinfo{15$^{th}$ Twente Student Conference on IT}{June 21$^{st}$, 2012, Enschede, The Netherlands.}
\CopyrightYear{2012} % Allows default copyright year (200X) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{New exchange model for child pornography analysis [abstract V1 | sec1 V9 | sec2 V7 | sec3 V7 | sec4 V5 | sec5 V2]}

\numberofauthors{1}
\author{
\alignauthor
Ruud Verbij \\
       \affaddr{University of Twente}\\
       \affaddr{P.O. Box 217, 7500AE Enschede}\\
       \affaddr{The Netherlands}\\
       \email{cp@ruudverbij.nl}
}
\date{12th of June 2012}

\maketitle
\begin{abstract}
This research concentrates around the topic of the criminal exchange of child pornography material on the Internet. The existing scientific material on this exchange lacks technical details that could help police detectives work more efficiently in child pornography cases. This research first takes a look at the existing literature on criminal child pornography exchange models. Thereafter it will look at the existing literature on new Internet based communication media, especially anonymization techniques. After this, a new criminal child pornography exchange model is presented and evaluated by interviewing police detectives concerned with online child pornography cases. The result of this research is a new criminal child pornography exchange model which allows for modeling anonymization within all the steps of the process. 
\end{abstract}

\keywords{child pornography, high tech crime, criminal exchange model}

\section{Introduction}
With the arrest of Robert M. in December 2010\cite{site:bbc} the Netherlands' police agency caught, allegedly, the biggest child abuser ever in the Netherlands. On his computer detectives found (hidden in a partially deleted TrueCrypt folder) 8 terabyte containing images and videos of child abuse. Along with the images and videos came the digital equivalent of 64.000 A4 papers containing chat logs with other child abusers, which led to the arrest of numerous of other child abusers in the Netherlands, Norway, Germany, the United States, Australia and many more countries. These arrests led to the question whether current detection methods used by police agencies to catch child abusers are still valid for the new internet era \cite{wijk2009achter}. The current detection methods are based upon exchange models of child pornography (CP) which may not really be adapted to this new era and therefore they may need to be revised. This research will try to answer the question of how to revise such exchange models to satisfy the need of police detectives for better analysis and detection methods.

Digital CP can be defined in multiple ways, this research will use a definition that is derived from the legal definition given by \cite{beech2008internet}, which cites the PROTECT Act of 2003:
\begin{quote}
	"...it is a crime to posses, manufacture or distribute pornography containing visual depictions of (a) a real child engaging in sexual acts or (b) a digital image, computer image, or computer generated image that is, or is indistinguishable from that of a minor engaged in sexually explicit conduct." from (18 U.S. Code Paragraph 2256(8) (B))
\end{quote}
This research acknowledges the legal definition of CP but it is not taking into account the issues related to computer generated images since they need to use different solutions than the ones discussed in the paper. Furthermore images and videos are widened to encompass digital material, leading to the following CP definition that is used by this research:
\begin{quote} 
	Digital child pornography is defined as digital pornography containing visual depictions of a real child engaging in sexual acts or a minor engaged in sexually explicit conduct. 
\end{quote}

To be able to describe the criminal process involved in the distribution, a type of model should be introduced to model the different steps involved in the process. This research will use Crime Schemes as proposed in \cite{willison2006understanding}. Steps in this process follow a flow. This means that certain processes depend on others, which need to be performed first. Groups of processes (categories) belong to each other and together form a category in the simplified model of the crime. In stealing a bike for example, there are different steps in how to break the lock, but they belong to each other and form the 'breaking the lock' category in the simplified model. Some different paths exist in breaking the lock, but it is always right to consider that one first needs to break the lock, before removing it from the bike. Since this research investigates exchange models and describe them via crime schemes, such an exchange model will from now on be called criminal exchange model.

Different authors have suggested that there should be more scientific research into the area of criminal exchange models of CP \cite{wijk2009achter, wolak2005child, zee2007kinderpornografische}. They conclude that most of what is known about the exchange of CP is due to successful arrests and that there are exchange methods (involving high tech components) which are not yet found by police detectives. Therefore new research must be conducted to gather more information on these high tech crime components in the exchange of CP which could then be included in the existing criminal exchange models.

The main research question in this research is 'How can the currently used main criminal exchange models of child pornography be adapted to describe (1) the current child pornography user behavior and (2) the new Internet based communication media used by child pornography offenders?'. This main research question is divided into four different subquestions:
\begin{enumerate}
	\item What are the currently used main criminal exchange models of CP?
	\item What are the main differences between the communication media used in the past and today in the exchange of CP?
	\item How can the changes associated with the current CP user behavior and the new internet based communication media be reflected in the currently used main criminal exchange models of CP? 
\end{enumerate}

The research questions (1) and (2) are answered using a literature study. Finally, research question (3) is answered by proposing a new CP criminal exchange model and by verifying it using interviews with police detectives that are concerned with the recent arrests of several child pornography offenders.

This paper is organized as follows. In section 2 an overview of the current criminal exchange models of CP is given. Furthermore, this section provides the answer of the research question (1). Section 3 provides the technical enhancements on the CP criminal exchange models, providing the answer to research question (2). In Section 4 a new CP criminal exchange model is proposed that is verified by using interviews with police detectives that are concerned with the recent arrests of several child pornography offenders.. Moreover, this section answers research question (3). Section 5 concludes and provides recommendations for future work.

\section{Child Pornography Exchange Models}
This section provides an overview of the current criminal CP exchange model. Furthermore, this section derives criteria and compares the discussed criminal CP exchange models.

Several papers and books briefly mention the exchange of CP, such as \cite{wolak2005child, jenkins2001beyond, webb2007characteristics}, which briefly focus on CP exchange via Internet, \cite{quayle2002paedophiles, beech2008internet}, which briefly focus on the CP exchange via usenet, bulletin boards or websites. However, only few of these papers that describe the CP exchange, 	go into more detail, see e.g. \cite{en2011phishing,wortley2006child,wijk2009achter,callanan2009internet}. The description level of detail used by papers is quite different and will therefore be elaborated in different sections.

However, only Faber et al. \cite{en2011phishing} provides a more complete description of a criminal CP exchange model. The other criminal CP exchange models discussed in this paper are derived by the author of this paper by carefully studying the information contained in the referenced papers and books.

In Table \ref{tables:exchangeModelsCompared} the different criminal CP exchange models are compared. These CP exchange models are compared using the following criteria:

\begin{itemize}
	\item Completeness of the criminal exchange model: this refers to the number of categories modeled by the criminal exchange model. 
		The steps defined in this research that need to be modeled by a criminal exchange model are:
		\begin{itemize}
			\item \textit{Production}: The physical abuse and the recording of it. Also location selection, victim recruiting, editing, lighting, restructuring of the video, etc. fall in this category since this research is not focused upon this category and only needs a way to model all processes that are not involved in the criminal exchange model.
			\item \textit{Hiding}: Hiding information that could lead to the producer or distributor, by using techniques such as encryption and stenography \cite{krone2005international}.
			\item \textit{Distribution}: Making CP material available for others to download/view.
			\item \textit{Downloading}: Downloading or streaming CP material.
			\item \textit{Storage}: Storing CP material and possibly hiding it.
		\end{itemize}
		In table \ref{tables:exchangeModelsCompared}, the grade ++ represents the situation that all the steps mentioned above are supported, while - - means that none of these steps are supported.
	\item Modeling of Anonymity: this refers to whether the criminal exchange model, models in detail the support of anonymity in the criminal CP process. Anonymity support refers to support of activities in such a way that the identity of the CP user cannot be detected. In table \ref{tables:exchangeModelsCompared}, the grade ++ represents the situation that a criminal exchange model provides all means to model Anonymity support. The grade - - represents the situation that the criminal exchange model does not  provide any means of modeling Anonymity support.
	\item Modeling of Distribution types: this refers to whether the criminal exchange model, models in detail the support of Distribution type in the CP process. Distribution type refers to the way of how the CP media is distributed. In table \ref{tables:exchangeModelsCompared}, the grade ++ represents the situation that a criminal exchange model provides all means to model the Distribution type. The grade - - represents the situation that the criminal exchange model does not provide any means of modeling the Distribution type.
	\item Transaction type: this refers to the type of transactions involved within the Criminal CP process. These transactions can be either Financial means (money) or CP interchange material. 
\end{itemize}

\subsection{Faber et al., 2011 \cite{en2011phishing}}
Figure \ref{fig:faber_01} gives the visual representation of the criminal CP exchange model proposed by \cite{en2011phishing}. This figure shows four different categories (\textit{Production},\textit{Hiding}, \textit{Distribution} and \textit{Storage}). \cite{en2011phishing} groups different steps in the process of the CP exchange. The step \textit{editing} is not included in such a group since it is not considered as being an important step in the criminal CP scheme.

Faber et al. \cite{en2011phishing} is the only research document that describes some sort of criminal exchange model for the criminal process of CP. This criminal CP exchange model \cite{en2011phishing} describes the process that is sketched in Figure \ref{fig:faber_01}. The \textit{Editing} event is just a video editing event and therefore it can be left out of the exchange model. The different types of steps that could be taken in the \textit{Coding} event are similar to what other authors have concluded (i.e. \cite{wortley2006child, jenkins2001beyond,wolak2005child}). It includes untraceability, invisibility, illegibility and unrecognizability. The \textit{Payment} event does not only involve cash payments, but also includes interchange of CP material which is found in several other articles as well (i.e. \cite{wortley2006child,wijk2009achter,wolak2005child}). The \textit{Distribution} event only covers the describing of different communication media such as newsgroups \cite{site:usenet}, bulletin boards \cite{site:bulletin}, P2P \cite{site:p2p}, e-mail, IRC \cite{site:IRC}, FTP \cite{site:FTP} and websites, but lacks to clarify the specifics for CP exchange on those communication media or the amount of usage on these different communication media. The authors of \cite{en2011phishing} make a clear distinction between the exchange via a website (acquire domain, acquire hosting and distribution) and exchange via other media (acquire costumers, payment, distribution). This is in clear contrast with different other papers, \cite{wortley2006child,wijk2009achter,callanan2009internet}, that all state that using a website to distribute CP always includes a payment.

\begin{figure}[ht]
\centering
\includegraphics[scale = 0.65, trim = 20 620 0 10]{images/Faber.pdf}
\caption{Part of the Crime Scheme as proposed by Faber et al. in \cite{en2011phishing}}
\label{fig:faber_01}
\end{figure}

The \textit{abuse recording} step is thoroughly described, covering topics as the severity of the recordings \cite{quayle2002paedophiles}, but it also covers topics such as the victim selection, grooming, consolidation, staff recruitment and location selection. The \textit{editing} step involves the anonymization of the abuse, making scenes, compiling it, making descriptions, etc. The \textit{acquire domain} and \textit{hosting} involve the process of getting a website and domain name to spread the material. This can be bought online using (stolen) credit cards, web money or servers that could be hacked. The \textit{acquire costumers} event describes the process of getting customers to find the CP material, in addition to websites, it involves mass mailing and it provides adds on the normal porn websites or getting inside costumers from fora or networks. The \textit{payment} event could be either money (using (stolen) credit cards, web money, billing companies) or interchange of CP material. The \textit{distribution} process involves the uploading and downloading of the CP material via virtual communities, news groups, fora, p2p, e-mail, chat, FTP and websites. The \textit{storage} step involves storing the material and hiding it from authorities and other users of that computer or network.

The processes modeled by Faber et al. involving the abuse and pre-abuse steps are in this research modeled to one process called \textit{abuse recording}, and therefore it is classified into the \textit{Production} category. The steps modeled in the process \textit{coding} are used to hide the producer's and distributor's identity and is therefore classified into the \textit{Hiding} category. The processes that cover the \textit{acquire costumers} steps and the steps of leading them to the CP material are grouped together with the actual distribution and payment processes to form the \textit{Distribution} category. The storage process modeled by Faber et al. is considered to be the \textit{Storage} category in this research.

Faber et al. elaborates thoroughly on the criminal CP exchange model and therefore are rated with a + on the completeness of the criminal model. The model lacks on providing details on modeling the anonymity and the ability to model Anonymity is therefore rated with a -. The up-to-date distribution media also lack and is therefore rated with a -. The types of transactions involved are both money and the interchange of CP material, see Table \ref{tables:exchangeModelsCompared}.

\subsection{Wortley et al., 2006 \cite{wortley2006child}}
Figure \ref{fig:wortley_01} provides the visual representation of the criminal CP exchange model proposed in \cite{wortley2006child}. This figure shows three different groups of processes (\textit{Production}, \textit{Distribution} and \textit{Downloading}).
Wortley et al. \cite{wortley2006child} emphasize that recent police activity on different open or semi-closed networks has led most CP users to change their communication means to more closed networks such as closed P2P networks, closed bulletin boards and closed chat rooms instead of websites, e-mail and newsgroups. Similar results are found in \cite{wijk2009achter, callanan2009internet}. Furthermore, Wortley et al. state that there are hardly any financial interactions involved within the process of distribution since almost all new material is produced by amateurs who do not seek financial gain in their child abuse. This resembles findings by other research activities (i.e., \cite{beech2008internet,wijk2009achter}) but it contradicts findings provided by, among others, the UN in 2006 (cited in \cite{wijk2009achter}). The UN stated that global CP exchange made about 6 billion dollar in 2005. Furthermore \cite{webb2007characteristics}, states that about 50\% of all CP users have paid to watch CP. The information provided by \cite{beech2008internet,wijk2009achter}, \cite{webb2007characteristics} show that there is a big market for CP exchange. Wortley et al., \cite{wortley2006child} lacks to provide the necessary details on the specifics on the different communication media for the CP exchange.

\begin{figure}[ht]
\centering
\includegraphics[scale = 0.65, trim = 20 720 0 25]{images/Wortley.pdf}
\caption{Derived Crime Scheme from Wortley et al. in \cite{wortley2006child}}
\label{fig:wortley_01}
\end{figure}

The \textit{production} process models the production of material, mostly made by amateurs but also covers professional recordings. The \textit{distribution} process describes in short the existence of pedophile rings or organized crime groups that interchange the CP material on different platforms like websites, e-mail, instant messages, newsgroups, bulletin boards, chat and p2p. The \textit{downloading} process describes the actual search for CP material by CP users. In \cite{wortley2006child} is stated that mass mailings and the ads on normal porn websites hardly exist anymore.

The process described by Wortley et al. as the \textit{production} process is modeled as the \textit{Production} category. The \textit{distribution} process is modeled as the \textit{Distribution} category and the \textit{downloading} process is modeled as the \textit{Downloading} category.

Wortley et al. do not elaborate thoroughly on the criminal CP exchange model, therefore the completeness of the criminal model is rated with a + / -. The modeling of Anonymity is not supported and therefore rated with a - -. The ability to model up-to-date distribution media is a little bit better and therefore rated with a -.  The type of transactions involved is only the interchange of CP material, see Table \ref{tables:exchangeModelsCompared}.

\subsection{Van Wijk et al., 2009 \cite{wijk2009achter}}
Figure \ref{fig:wijk_01} depicts the visual representation of the criminal exchange model provided by \cite{wijk2009achter}. This figure shows four different groups of processes (\textit{Production}, \textit{Distribution}, \textit{Downloading} and \textit{Storage}).

Van Wijk et al. \cite{wijk2009achter} describes four different types of distribution; commercial distribution (via mail delivery), commercial websites (pay by credit card or emoney), open networks (open IRC channels, open P2P networks, open bulletin boards) and closed networks (chat, e-mail, closed bulletin boards and closed P2P networks). Because of recent police activity against CP, more or less all distribution is in the last category, see \cite{wortley2006child, callanan2009internet}. Van Wijk et al. takes a closer look into the high tech components involved in the \textit{distribution} process. However, the focus is more on the CP downloaders instead of being on the CP distributors. Some of the mentioned high tech components involve (1) virtual hard drives to browse without leaving traces on the computer \cite{site:VHD}, (2) the use of disk encryption software to hide downloaded material on specific parts of the hard drive \cite{site:diskenc}, (3) the use of proxy servers as storage locations or to browse anonymously \cite{site:proxy} and (4) software to erase a hard drive.

\begin{figure}[ht]
\centering
\includegraphics[scale = 0.65, trim = 20 650 0 0]{images/VanWijk.pdf}
\caption{Derived Crime Scheme from Van Wijk et al. in \cite{wijk2009achter}}
\label{fig:wijk_01}
\end{figure}

The process described by Van Wijk et al. as \textit{production} is mentioned in the model, but no further information is given about this step. The \textit{distribution} step is different from earlier models and elaborates more on the different distribution media. The distribution is split in four different types of distribution.
\begin{itemize}
	\item Commercial distribution: uses post-order to order CP material online and receive it by post mail. 
	\item Commercial websites: websites that run on servers mostly located in eastern European cities, which are distributing the CP material by selling it online.
	\item Open networks: networks, which can be used to distribute CP material without requiring any password or security protection. Such open networks are: open P2P networks, open chat rooms and open bulletin boards.
	\item Closed networks: networks that can be used to distribute CP material using the same media as the open networks, but which are closed by using password and security protection, such as encryption and decryption.
\end{itemize}

The \textit{production} process is modeled as the \textit{Production} category. The different distribution media are grouped together as the \textit{Distribution} category since all these distribution media types involve the characteristics of this category. The \textit{downloading} process is modeled as the \textit{Downloading} category and the \textit{storage} process is modeled as the \textit{Storage} category.

Van Wijk et al. elaborates on the criminal exchange model and the completeness of the criminal model is therefore rated with a+. It also presents some details on the Anonymity support and that is therefore rated a +. The ability to model up-to-date distribution media is relatively extensive and therefore rated with a +. The types of transactions involved are encompassing both money and interchange of CP material, see Table \ref{tables:exchangeModelsCompared}.

\subsection{Callanan et al., 2009 \cite{callanan2009internet}}
Figure \ref{fig:callanan_01} depicts the visual representation of the criminal exchange model provided in \cite{callanan2009internet}. This figure shows two different groups of processes (\textit{Downloading} and \textit{Distribution}).

Callanan et al. \cite{callanan2009internet} describes different communication media used to distribute CP material than the other CP exchange models described in the previous subsections. In particular, \cite{callanan2009internet} describes Freenet \cite{site:freenet} as a way to distribute CP material in encrypted and sliced packets which are then on a P2P manner distributed to users of Freenet (including non CP users). Freenet supports multiple anonymity options, making it possible to easily hide the identity of its users. Furthermore, \cite{callanan2009internet} describes several characteristics of Usenet system and the incentives of why this system is used among CP users. Both these communication media (i.e., \textit{distribution} process) have the characteristic that it is really hard to delete the CP material once it has been distributed.

\begin{figure}[ht]
\centering
\includegraphics[scale = 0.65, trim = 20 690 0 40]{images/Callanan.pdf}
\caption{Derived Crime Scheme from Callanan et al. in \cite{callanan2009internet}}
\label{fig:callanan_01}
\end{figure}

The hiding identity process describes different communication media that could be used either by downloaders of distributors for the exchange of CP. The actual downloading process models anonymity support by those communication media. The distribution process describes the anonymity support offered to distributors of CP material.

\cite{callanan2009internet} describes various methods of identity hiding, which in turn could be used for downloading and/or distribution. The \textit{hiding} identity process describes different communication media that could be used by either CP material downloaders or CP material distributors. The actual \textit{downloading} process encompasses the anonymity support used by those communication media. The \textit{distribution} process encompasses the anonymity support offered to distributors of CP material. The \textit{hiding identity} process as modeled by Callanan et al. cannot be classified on any of the categories introduced at the introductory part of this section. In particular, this process encompasses both the identity hiding of CP material downloaders and CP material distributors. The \textit{downloading} process is modeled as the \textit{Downloading} category and the \textit{distribution} process is modeled as the \textit{Distribution} category.

Callanan et al. does not elaborate on the criminal exchange model and the completeness of the criminal model is therefore rated a -. The detailed description of Anonymity support is rated with a + +. The detailed description of up-to-date distribution media is also rated with a + +, since it is very elaborative. The types of transactions involved are not discussed, see Table \ref{tables:exchangeModelsCompared}.

\subsection{Conclusion}
A comparison between the criminal CP exchange models described in this section is depicted in Table \ref{tables:exchangeModelsCompared}. The criteria used for this comparison are given in the introductory part of section 2.1.
From this table it can be seen that the only detailed criminal CP exchange model is found in only \cite{en2011phishing}. The components by this model are also mentioned by other authors as well, except for the lack of payment in distribution via websites, which is not covered in \cite{en2011phishing}. The amount of usage of different communication media has made a switch from open networks to more closed ones as found by \cite{wortley2006child,wijk2009achter}. The types of CP payment methods mentioned in the exchange models differ. Though, it can be stated that the more advanced a CP user is, the less likely he/she will favorit paying for CP material. In particular, he/she will be far more interested in interchanging CP material, and thereby becoming more and more important in the online world of CP exchange \cite{wijk2009achter,quayle2002paedophiles,krone2005international,en2011phishing}. \cite{wijk2009achter} describes several high tech components involved in the CP material \textit{downloading} process and its \texttt{distribution} (virtual hard disks, disk encryption software and proxy servers). \cite{callanan2009internet} describes in more detail several communication media types (Usenet and Freenet) and the anonymity support used for the actual CP material distribution. However, \cite{callanan2009internet} is not providing any information on the used transaction types. \cite{en2011phishing} and \cite{wijk2009achter} use both Money and Interchange of CP material as transaction types, while \cite{wortley2006child} uses only the interchange of CP material as transaction type.

\begin{table}[!ht]
\caption{Comparison of current criminal CP exchange models}
\begin{tabular}{|p{0.16\columnwidth}||p{0.15\columnwidth}|p{0.15\columnwidth}|p{0.15\columnwidth}|p{0.20\columnwidth}|}
\hline
\begin{sideways} \parbox{30mm}{\centering Author} \end{sideways} & \begin{sideways} \parbox{30mm}{\centering Completeness of the criminal exchange model} \end{sideways} & \begin{sideways} \parbox{30mm}{\centering Modeling of Anonymity} \end{sideways} &  \begin{sideways} \parbox{30mm}{\centering Modeling of Distribution types} \end{sideways} & \begin{sideways} \parbox{30mm}{\centering Transaction type} \end{sideways} \\ \hline & \\[-1em]\hline
Faber et al. \cite{en2011phishing} & + & - & - & Money and interchange \\ \hline
Wortley et al. \cite{wortley2006child} & +/- & - - & -  & Interchange \\ \hline
Van Wijk et al. \cite{wijk2009achter}   & + & + & + & Money and interchange \\ \hline
Callanan et al. \cite{callanan2009internet}   & - & + + & + + & Not discussed \\ \hline
\end{tabular}
\label{tables:exchangeModelsCompared}
\end{table}

\section{Enhancements of CP exchange model components}
This section describes the ongoing technical enhancements on the CP criminal exchange models. The technical enhancements that will be discussed in this section will also be rated on the scale that the different criminal exchange models were rated on in section 2. The results can be found in Table \ref{tables:dataExchangeCompared}.

\subsection{The Onion Routing (TOR)}
Routing traffic through different hops is a method of anonymizing internet browsing and has been used for several years \cite{patil1963high}. In 2004, Dingledine et al. \cite{dingledine2004tor} proposed the so called The Onion Routing (TOR) protocol in which traffic is routed through three different hops and is encrypted in such a way that hops along the way can only see the identity of the previous hop as being the sender and the identity of the next hop as being the destination. In other words the intermediate hops cannot see the identity of the sender that created the packet and the identity of the receiver where the generated packet was addressed to. This provides in principle maximum anonymity since hop1 only knows the sender and hop2, hop2 only knows hop1 and hop3 and hop3 only knows hop2 and the final destination. None of the hops are able to know both the sender and the receiver of the internet traffic. Since the encryption standards and security protocols are verified \cite{goldberg2006security} to be secure if used properly, this could provide high anonymity for CP users. Furthermore, \textit{TOR} provides the so called 'hidden services'. Hidden services are websites that can only be accessed if their address is known (being a 16 character wide random address). The location of the hidden services remains a secret since accessing the address is provided through a rendezvous point. Connections from the rendezvous point to the sender or receiver are done through \textit{TOR} (and thus uses at least three hops). Visiting such hidden services is done by connecting to a rendezvous point through \textit{TOR} (meaning that the rendezvous does not know who the sender is), which than opens a connection to the hidden services through \textit{TOR} (meaning that hidden services doesn't know who the rendezvous point is). It could therefore be deduced that both the sender and the hidden service are not able to know the identity of the opponent. This also holds for the rendezvous point. This could stimulate CP users to upload and share CP material using hidden services that are specially designed for CP. In that way distributors and downloaders of CP are considered to be completely anonymous.

\textit{TOR} is able to support various categories of the CP criminal exchange model, namely \textit{Hiding}, \textit{Distribution}, \textit{Downloading} and \textit{Storage}. This is rated with a + for the completeness of the criminal exchange model, see Table \ref{tables:dataExchangeCompared} since \textit{Production} step is not included in this model. The support of Anonymity and Distribution methods are both graded with a + +, since they can be well provided by the hidden services.

\subsection{Freenet}
\textit{Freenet} \cite{clarke2001freenet} provides similar features as the hidden services provided by \textit{TOR}. The exception is that everybody is partly able to share the hidden service. Freenet is a P2P-service which routes and disseminates requests, uploads and downloads among different users in chunks \cite{clarke2001freenet}. All chunks are requested through different hops and are therefore spread anonymously. All content is encrypted and chopped into chunks before spread through the network. Freenet can be used in either Darknet mode or Opennet mode, where networks are based upon friends only or on the entire user base, respectively.

Freenet is able to model various categories of the CP criminal exchange model, namely \textit{Hiding}, \textit{Distribution} and \textit{Downloading}. Since rarely requested parts disappear in the network, the \textit{Storage} category does not apply to Freenet. This is rated with a + / - for the completeness of the criminal exchange model, see Table \ref{tables:dataExchangeCompared}. The Anonymity that can be modeled along with the Distribution methods offered provide both criteria's with a + +.

\subsection{Anonymous remailers}
Normal email traffic can be subject of investigation since the source address is exposed, leading to loss of anonymity. To regain this level of anonymity, anonymous remailers can be used, see e.g. \cite{danezis2003mixminion}. In general, they are used to forward an email to someone anonymously by stripping all identifiable information of the email leaving nothing but the bare text and the receiver. Some of these remailers offer additional features such as the ability of two-way communication by storing lists of senders and their email addresses (though, this is hazardous information that is being stored). Since this could still lead to the threat of being discovered by applying traffic analysis, Mixminion remailers can be used \cite{danezis2003mixminion}. This type of remailers take notion of the traffic analysis characteristics and use multi-hops to forward emails using e.g., delays and encryption.

\textit{Anonymous remailers} is able to support the distribution of CP material and the recruitment of costumers for CP websites. Since these processes are only involved in the Distribution, this is graded with a - - for the completeness of the criminal exchange model. Different design techniques of these remailers offers different levels of anonymity; it is often not very clear who runs a remailer and if it has not yet been hacked. It therefore can only get a grade of + for the ability of modeling anonymity. The number of distribution methods is not increased with the introduction of anonymous remailers, though, one of them (email) has been extended, it is therefore rated as a - on the modeling of distribution, see Table \ref{tables:dataExchangeCompared}.

\subsection{TrueCrypt}
\textit{TrueCrypt} is an on-the-fly encryption tool that can be used to encrypt either parts or complete harddisks. \textit{TrueCrypt} uses very strong cryptographic principles \cite{miao2010research} by which it can provide strong privacy if strong keys are used. TrueCrypt can thus be used to encrypt parts of the harddisk containing CP material for storage. Furthermore, \textit{TrueCrypt} offers the option to use hidden volumes within such an encryption partition. It is very difficult to detect and prove the existence of such a hidden volume, and it therefore provides plausible deniability of that hidden volume. A CP user could for example reveal the body of an encrypted partition which contains somewhat sensitive information, creating the plausible deniability for a hidden volume within the encrypted partition.

Since \textit{TrueCrypt} only gives the possibility to model \textit{Storage}, it is rated with a - - on completeness of the exchange model. The plausible deniability makes it possible to rate with a + + on the ability to model anonymity. \textit{TrueCrypt} does not provide any support for CP material distribution and therefore it is rated with a - - on the modeling of distribution, see Table \ref{tables:dataExchangeCompared}.

\subsection{Anonymous credit cards}
Paying for CP material has been declining according to some research results \cite{wortley2006child,wijk2009achter,beech2008internet} since police investigators have been investigating the flow of money to get a hold on downloaders of CP. Due to this fact, CP distributors who were in the business only for financial reasons have disappeared and the transaction type of exchange has been changed to interchange of CP material.

\textit{Anonymous credit cards} can be used to perform a transaction that involves CP exchange anonymously. These credit cards can be bought using cash and can be used to perform payments online and offline. Furthermore, they can be used to perform transactions from other (anonymous) credit cards or stolen credit cards. This could be used to buy CP material online anonymously, without the possibility of tracing the transaction \cite{wall2007cybercrime}. Therefore, this can be considered as being a new burst for commercial CP material distributed from countries with a lack of legislation on CP \cite{kierkegaard2008cybering}.

\textit{Anonymous credit cards} only enhances the \textit{Distribution} category and is therefore rated with a - - on the completeness of the exchange model, see Table \ref{tables:dataExchangeCompared}. The anonymity that could possibly be modeled with anonymous credit cards is quiet strong, though, these credit cards infer a few risks when used other than in the CP process. It is therefore rated with a + on the ability to model anonymity. Since distribution methods are not enhanced, but only the payment method, the ability to model distribution is rated with a - -.

\subsection{Webcam hacking}
There have been reports \cite{mishna2009ongoing,salomon2010examples} of viruses that can turn webcams on without that the user of the computer knowing. This could lead to serious problems within the \textit{Abuse recording} process, e.g. with grooming and consolidation being easier if children are confronted with secretly recorded images or videos.

These \textit{Webcam hacks} only enhances the \textit{Production} category and are therefore rated with a - - on the completeness of the exchange model, see Table \ref{tables:dataExchangeCompared}. The anonymity that could possibly be modeled with \textit{Webcam hacks} is quiet strong, it is rated with a + on the modeling of Anonymity. The Distribution modeling is not supported by \textit{Webcam hacks} and is rated with a - -.

\begin{table}[!ht]
\caption{Comparison of enhanced exchange methods}
\begin{tabular}{|p{0.19\columnwidth}||p{0.15\columnwidth}|p{0.15\columnwidth}|p{0.15\columnwidth}|p{0.17\columnwidth}|}
\hline
\begin{sideways} \parbox{30mm}{\centering Technique} \end{sideways} & \begin{sideways} \parbox{30mm}{\centering Completeness of the criminal exchange model} \end{sideways} & \begin{sideways} \parbox{30mm}{\centering Modeling of Anonymity} \end{sideways} &  \begin{sideways} \parbox{30mm}{\centering Modeling of Distribution types} \end{sideways} & \begin{sideways} \parbox{30mm}{\centering Transaction type} \end{sideways} \\ \hline & \\[-1em]\hline
TOR \cite{dingledine2004tor} & + & + + & + + & Not discussed \\ \hline
Freenet \cite{clarke2001freenet} & +/- & + + & + +  & Not discussed \\ \hline
Anonymous remailers \cite{danezis2003mixminion} & - - & + & - & Not discussed \\ \hline
TrueCrypt \cite{miao2010research}   & - - & + + & - - & Not discussed \\ \hline
Anonymous credit cards \cite{wall2007cybercrime}   & - - & + & - - & Money \\ \hline
Webcam hacks \cite{mishna2009ongoing,salomon2010examples}   & - - & + & - - & Not discussed \\ \hline
\end{tabular}
\label{tables:dataExchangeCompared}
\end{table}

\section{Proposed Exchange Model}
This section proposes a new CP criminal exchange model (Section 4.1 and 4.2) that is verified by the use of interviews with police detectives that are concerned with the recent arrests of several child pornography offenders (Section 4.3).

\subsection{Specification}
A new criminal CP exchange model should be able to integrate most of the exchange models described in Sections 2 and 3. 
Since the exchange model proposed by Faber et al. \cite{en2011phishing} provides the most complete criminal exchange model, it will be used as the main framework, see Figure \ref{fig:faber_01}.

Some research results contradicted specific details of actions in the CP exchange model proposed by Faber et al. \cite{quayle2002paedophiles,krone2005international}. Furthermore, \cite{wijk2009achter} proposed to classify the distribution methods into four different categories of distribution. The \textit{Downloading} category was included in multiple CP exchange models (see Figures \ref{fig:callanan_01}, \ref{fig:wijk_01} and \ref{fig:wortley_01}) but was not present in Faber et al.'s model.
These differences have been added to the original CP exchange model proposed by Faber et al., see Figure \ref{fig:newModel}.

The step that is missing in the CP exchange model of Faber et al. and is strongly supported in other exchange models, e.g., in Callanan et al. \cite{callanan2009internet} TOR and Freenet, is related to Anonymity support. Therefore, the proposed exchange model will enhance the CP exchange model proposed by Faber et al. with the process \textit{Anonymity support}, see Figure \ref{fig:newModel}. As can be seen the \textit{Anonymity support} process impacts all other processes. This is due to the fact that Anonymity support can be applied on any of the CP exchange model processes proposed by Faber et al.
In addition to this enhancement, each of the processes/steps encompassed in the enhanced CP exchange model should also include all possible known alternatives that can be used to realize the process. 
Based on the information provided in Sections 2 and 3, we distinguish the following alternative solutions per each process of the enhanced CP exchange model.
\subsubsection{Production}
The possible alternative solutions that can be used to fulfill the \textit{Production} category and are described in Sections 2 and 3 are the following:
\begin{itemize}
	\item Abuse recording, see Section 2.1 and 3.6.\\
		Abuse recording and the used solutions can be found in Faber et al. \cite{en2011phishing}. An additional solution that can be classified in the \textit{Abuse recording} process is the \textit{Webcam hacking} described in \cite{mishna2009ongoing,salomon2010examples}.
\end{itemize}

\subsubsection{Hiding}
The possible alternative solutions that can be used to fulfill the \textit{Hiding} category and are described in Sections 2 and 3 are the following:
\begin{itemize}
	\item Coding, see Section 2.1.\\
		Coding solutions can be found in Faber et al. \cite{en2011phishing}. The described features by Faber et al. are more elaborated in \cite{wortley2006child, jenkins2001beyond,wolak2005child}.
		\begin{itemize}
			\item \textit{Untraceability}: the disguise of the origin of the CP material. This mainly describes the deletion of metadata of a file.
			\item \textit{Invisibility}: the disguise of CP material without the use of external software. This mainly describes the altering of file extensions and filenames.
			\item \textit{Illegibility}: the encryption of CP material.
			\item \textit{Unrecognizability}: the disguise of CP material with the use of external software. This mainly describes the stenography used to hide CP material inside other files and traffic.
		\end{itemize}
\end{itemize}

\subsubsection{Distribution}
The possible alternative solutions that can be used to fulfill the \textit{Distribution} category and are described in Sections 2 and 3 are the following:
\begin{itemize}
	\item Acquire domain and hosting, see Section 2.1\\
		Acquire domain and hosting are described by Faber et al. \cite{en2011phishing}.
	\item Acquire customers, see Section 2.1, 2.2, 2.3 and 3.3.\\
		The acquiring of customers is described by Faber et al., Wortley et al., Van Wijk et al. \cite{en2011phishing, wortley2006child, wijk2009achter} and is enhanced by the use of \textit{Anonymous remailers} \cite{wall2007cybercrime}.
	\item Payment, see Sections 2.1, 2.3, 3.1, 3.2 and 3.5.\\
		Payment is originally described by Faber et al. \cite{en2011phishing} as financial transaction (money) and interchange of CP material, Van Wijk et al. In particular \cite{wijk2009achter} elaborates and motivates the use of payment and interchange of CP material. Both processes are enhanced by the use of \textit{TOR} \cite{dingledine2004tor}, \textit{Freenet} \cite{clarke2001freenet} and \textit{Anonymous credit cards} \cite{wall2007cybercrime}.
	\item Distribution, see Sections 2.1, 2.2, 2.3, 2.4, 3.1, 3.2 and 3.3.\\
		Distribution is roughly described by Faber et al., Wortley et al. and Van Wijk et al. \cite{en2011phishing,wortley2006child,wijk2009achter} and is more elaborated by Callanan et al. \cite{callanan2009internet}. This process is enhanced by the use of \textit{TOR} \cite{dingledine2004tor}, \textit{Freenet} \cite{clarke2001freenet} and \textit{Anonymous remailers} \cite{wall2007cybercrime}.
\end{itemize}

\subsubsection{Downloading}
The possible alternative solutions	 that can be used to fulfill the \textit{Downloading} category and are described in Sections 2 and 3 are the following:
\begin{itemize}
	\item Downloading, see Sections 2.2, 2.3, 2.4, 3.1 and 3.2.\\
		Downloading is only briefly mentioned by Wortley et al. \cite{wortley2006child}, Callanan et al. In particular, \cite{callanan2009internet} elaborate this process in more detail. Characteristics of downloaders are described by Van Wijk et al.\cite{wijk2009achter}. The enhancements introduced by \textit{TOR} \cite{dingledine2004tor} and \textit{Freenet} \cite{clarke2001freenet} can also be applied to this process.
\end{itemize}

\subsubsection{Storage}
The possible alternative solutions that can be used to fulfill the \textit{Storage} category and are described in Sections 2 and 3 are the following:
\begin{itemize}
	\item Storage, see Sections 2.1, 2.3 and 3.4.\\
		Storage is briefly described by Faber et al. \cite{en2011phishing}. Van Wijk et al. \cite{wijk2009achter} describes this process in more detail and introduces some aspects of \textit{physical storage}. \textit{TrueCrypt} \cite{miao2010research} enhances this process.
\end{itemize}

\subsubsection{Anonymity support}
The possible alternative solutions that can be used to fulfill the ongoing \textit{Anonymity support} and are described in Sections 2 and 3 are the following:
\begin{itemize}
	\item Production
		\begin{itemize}
			\item Webcam hacks, see Section 3.6.\\
				\textit{Webcam hacks} \cite{mishna2009ongoing,salomon2010examples} provides anonymity for producers of CP material. Producers can groom and consolidate children into recording CP material using their own webcam if they are confronted with secretly recorded material by the producer earlier.
		\end{itemize}
	\item Hiding
		\begin{itemize}
			\item Hiding identity, see Section 2.1.\\
				\textit{Unrecognizability}, \textit{illegibility}, \textit{invisibility} and \textit{untraceability} of CP material provide additional anonymity for the producer of this CP material \cite{en2011phishing}. These techniques can be used to hide the identity of the producer before it gets distributed to a distributer.
		\end{itemize}
	\item Distribution
		\begin{itemize}
			\item \textit{Anonymous credit cards}, see Section 3.5.\\
				\textit{Anonymous credit cards} \cite{wall2007cybercrime}: provides additional anonymity for distributers to register their domain and hosting. It also enhances the payment process.
			\item \textit{Anonymous remailers}, see Section 3.3.\\
				\textit{Anonymous remailers} \cite{wall2007cybercrime}: provides additional anonymity for distributers to acquire customers for their commercial CP website.
			\item \textit{TOR}, see Section 3.1.\\
				\textit{TOR} \cite{dingledine2004tor}: provides additional anonymity for costumers of commercial CP websites. It furthermore enhances the anonymity of other CP related internet surfing.
			\item \textit{Hidden services} by \textit{TOR}, see Section 3.1.\\
				\textit{TOR} \cite{dingledine2004tor}: provides additional anonymity for distributors of CP material.
			\item \textit{Freenet} (Darknet mode), see Section 2.4 and 3.2.\\
				\textit{Freenet} \cite{clarke2001freenet, callanan2009internet}: provides additional anonymity for distributors of CP material.
		\end{itemize}
	\item Downloading
		\begin{itemize}
			\item \textit{TOR}, see Section 3.1.\\
				\textit{TOR} \cite{dingledine2004tor}: provides additional anonymity for downloaders / viewers of CP material.
			\item \textit{Freenet} (Darknet mode), see Section 2.4 and 3.2.\\
				\textit{Freenet} \cite{clarke2001freenet,callanan2009internet}: provides additional anonymity for downloaders of CP material.
		\end{itemize}
	\item Storage
		\begin{itemize}
			\item textit{Storage}, see Section 3.4.\\
				\textit{TrueCrypt} \cite{miao2010research}: provides additional anonymity for the storage of CP material.
		\end{itemize}
\end{itemize}
Several processes in the proposed criminal CP exchange model can be modeled in combination with the Anonymity support process, see Figure \ref{fig:newModel}.

\subsection{Graphical representation}
This section describes how the reader should interpret the graphical representation in Figure \ref{fig:newModel}. The graphical representation of the model is roughly built as an activity diagram as proposed by the UML standard \cite{eriksson2000business}. The process starts with the closed circle on the left going to the first category, namely \textit{Production}. Each arrow represents the closure of one step and the beginning of a new one (the start and the end of the arrow respectively). After the first few processes, there is a branch / choice (drawn as a black rectangle) after which there are three different methods of distribution. The post-order distribution is not included in this research. After the \textit{Distribution}, \textit{Downloading} and \textit{Storage} categories, the steps end in the closed circle with the open circle around it.

\begin{figure*}[ht]
\centering
\includegraphics[scale = 0.8, trim = 0 530 0 0]{images/newModel.pdf}
\caption{Proposed criminal CP exchange model}
\label{fig:newModel}
\end{figure*}

\subsection{Verification}
The verification of this newly proposed criminal CP exchange model is done by interviewing seven police detectives involved in the recent CP cases in the Netherlands. They belong to the Netherlands' police agency (govermental police agency). The detectives that have been interviewed have different backgrounds in CP or IT studies.

In general the police detectives agree with the newly structured sequence of events in the criminal CP exchange process. They see it as a valuable addition to the earlier proposed exchange model by Faber et al. \ref{fig:faber_01} that the different distribution methods are split according to results by Van Wijk et al. \ref{fig:wijk_01}. The police detectives are not convinced that the \textit{Editing} process is not included in the \textit{Hiding} category. They argue that the \textit{Editing} process also involves the masking of the child abuser and therefore belongs to the \textit{Hiding} category.

The results of the interview with the police detectives about the new proposed exchange model are analysed and given below:
\begin{itemize}
	\item \textit{Production}\\
		\textit{Abuse recording}: The use of abuse recording step defined by Faber et al. \cite{en2011phishing} found by the detectives to be modeled satisfactorily enough in order to describe the \textit{Production} process. The enhancement described by the \textit{Webcam hacking} \cite{mishna2009ongoing,salomon2010examples} has not been observed by the interviewed police detectives in practice (i.e. during their daily work) yet. Though, colleague detectives from foreign countries have observed child abusers chatting about this option, but it is not certain whether it has really happened and used in practice.
	\item \textit{Hiding}\\
		\textit{Coding}: The mentioned techniques deduced from Faber et al. \cite{en2011phishing} \textit{untraceability}, \textit{invisibility}, \textit{illegibility} and \textit{unrecognizability} are partly recognized by the police detectives. In particular, they have observed several of cases in practice where the encryption (\textit{illegibility}) and deletion of metadata (\textit{untraceability} have been used. The use of external software (stenography in \textit{unrecognizability}) though, is hardly observed in practice.
	\item \textit{Distribution}
		\begin{itemize}
			\item \textit{Acquire domain and hosting}: these processes are observed by police detectives in practice, though, only in foreign countries. Up to now, the police have not seen any cases in which Dutch CP users have registered Internet based domains and hosting to build a commercial CP website. The information deduced from Faber et al. \cite{en2011phishing} is found as being accurate, since the detectives have observed this activity also in practice.
			\item \textit{Acquire customers}: as with the \textit{Acquire domain and hosting} processes, police detectives were only aware of foreign cases in which the active \textit{acquiring of customers} is observed. The use of \textit{Anonymous remailers} as suggested by the enhancements though, has not yet been observed in practice.
			\item \textit{Payment}: as with the \textit{Acquire domain, hosting and customers} processes, police detectives were only aware of foreign cases in which the receiving of \textit{Payments} were processed. Though, there are cases in which Dutch CP users have paid to watch CP material on commercial websites and where in all of these cases, \textit{credit card payments} or different \textit{emoney payments} were made. The enhancement proposed by the \textit{Anonymous credit cards} have not been observed by the police detectives, in practice. The detectives do not expect to see this activity happening in the future in the Netherlands since buying such \textit{Credit Cards} in the Netherlands is really hard.
			\item \textit{Distribution}: the distribution that is proposed by Faber et al., Wortley et al. and Van Wijk et al. \cite{en2011phishing, wortley2006child, wijk2009achter} are found by the detectives to be outdated. The new distribution methods are far more anonymized (e.g., Freenet \cite{clarke2001freenet} and TOR hidden services \cite{dingledine2004tor}). Therefore the proposed enhancements are found to be very valuable. Usenet, Fora, FTP, e-mail, etc. are not anymore being observed by police detectives in their daily police activities.
		\end{itemize}
	\item \textit{Downloading}\\
		\textit{Downloading}: the police detectives emphasized that the most of the downloading takes place anonymously since the \textit{distribution} only prescribe downloading methods that are anonymous. Among them are browsing with the use of \textit{TOR} \cite{dingledine2004tor} and downloading CP material with the use of \textit{Freenet} \cite{clarke2001freenet}. The police detectives emphasized that the characteristics that are described by Van Wijk et al. \cite{wijk2009achter} give a valuable insight into the group of CP users.
	\item \textit{Storage}\\
		\textit{Storage}: the police detectives expected an elaborated description on the categorization obsession of CP material downloaders. The obsession is roughly described by Van Wijk et al. \cite{wijk2009achter} in the \textit{Downloading} process, but it could also be stretched/placed to the \textit{Storage} process, since it influences the way the storage of CP material is arranged. The enhancement of the \textit{Storage} process with the use of \textit{TrueCrypt} is sometimes observed in practice, but not often.
\end{itemize}

\section{Conclusions and Future Work}
This paper focussed on how the currently used main criminal exchange models of child pornography can be adapted in order to describe (1) the current child pornography user behavior and (2) the new Internet based communication media used by child pornography offenders. Several research questions are derived and are answered by this paper.

Section 2 answers research question (1), by describing four different criminal CP exchange models \cite{en2011phishing, wortley2006child, wijk2009achter, callanan2009internet}. Faber et al. \cite{en2011phishing} is the most elaborated model.

Section 3 answers research question (2), by providing the technical enhancements on the CP criminal exchange models. In particular, six different enhancements to the existing CP exchange models were given, including \textit{The Onion Routing}, \textit{Freenet}, \textit{Anonymous remailers}, \textit{TrueCrypt}, \textit{Anonymous credit cards} and \textit{Webcam hacks}.

Section 4 answers research question (3) by proposing a new criminal CP exchange model that is verified by using interviews with police detectives of the Netherlands' police agency that are concerned with the recent arrests of several child pornography offenders. The newly proposed CP exchange model has found its basis in the model proposed by Faber et al. \cite{en2011phishing} since this is the most elaborated one.

The enhancements made to the model by Faber et al. include (1) process enhancements and (2) technical enhancements. The process enhancements make it clearer that there is a distinction between three different distribution techniques: commercial websites, post-order and open / closed networks. The technical enhancements model is related to the Anonymity support that is omitted in the model proposed by Faber et al. \cite{en2011phishing} and other researches. By analyzing these enhancements, including  the earlier proposed anonymization techniques, it could be deduced that \textit{Anonymity} impacts all processes available in the criminal CP exchange model.

Future work includes three major research activities that could be undertaken. First of all, the list of enhancements proposed in Section 3 of this research is far from complete. They are found by the mere creativity of the author and could be researched more thoroughly (possibly including police detectives). The verification of the proposed model should be performed more thoroughly. This could be done using case studies based on real police cases, or by interviewing a higher number of police detectives, e.g. from local police agencies or from other countries.
Finally, the effectiveness of this new proposed model should be measured in practice.

\bibliographystyle{abbrv}
\bibliography{paper}
\vspace{50 mm}
%APPENDICES are optional

\balancecolumns
\end{document}

### 2013-05-22 paper.tex
New paper

@@
-% This is "bach-ref-2009.tex" Updated january 29th 2010.
-% This file should be compiled with "sig-alternate-fixed.cls" January 2010.
-% It is based on the ACM style "sig-alternate.cls"
-% -------------------------------------------------------------------------
-% This example file demonstrates the use of the 'sig-alternate-fixed.cls'
-% V2.5 LaTeX2e document class file. It is for those submitting
-% articles to the Twente Student Conference on IT. Both this file as the 
-% document class file are based upon ACM documents.
-%
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls) produces:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line TSConIT
-%       4) NO page numbers
-%       5) NO headers and/or footers
-%
-%
-% Using 'sig-alternate.cls' you have control, however, from within
-% the source .tex file, over both the CopyrightYear
-% (defaulted to 200X) and the ACM Copyright Data
-% (defaulted to X-XXXXX-XX-X/XX/XX).
-% e.g.
-% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
-% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
-%
-% ---------------------------------------------------------------------------------------------------------------
-% This .tex source is an example which *does* use
-% the .bib file (from which the .bbl file % is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission, you *NEED* to 'insert'
-% your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
+\documentclass[10pt,conference,a4paper]{IEEEtran}
 
-% refers to the cls file being used
-\documentclass{sig-alternate-br}
+%import packages here
+\usepackage{amsmath}
+\everymath{\displaystyle}
+\usepackage{graphicx}
+\usepackage{caption}
+\graphicspath{{Images/}}
 
-\usepackage{graphicx}
-\usepackage{rotating}
+\title{Internet Attribute Certificate Profile for Authorization - An Analyses}
+\author{Ruud Verbij}
+%begin document
+\begin{document}
+\maketitle
 
-\begin{document}
-%
-% --- Author Metadata here --- DO NOT REMOVE OR CHANGE 
-\conferenceinfo{15$^{th}$ Twente Student Conference on IT}{June 21$^{st}$, 2012, Enschede, The Netherlands.}
-\CopyrightYear{2012} % Allows default copyright year (200X) to be over-ridden - IF NEED BE.
-%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
-% --- End of Author Metadata ---
-
-\title{New exchange model for child pornography analysis [abstract V1 | sec1 V9 | sec2 V7 | sec3 V7 | sec4 V5 | sec5 V2]}
-
-\numberofauthors{1}
-\author{
-\alignauthor
-Ruud Verbij \\
-       \affaddr{University of Twente}\\
-       \affaddr{P.O. Box 217, 7500AE Enschede}\\
-       \affaddr{The Netherlands}\\
-       \email{cp@ruudverbij.nl}
-}
-\date{12th of June 2012}
-
-\maketitle
 \begin{abstract}
-This research concentrates around the topic of the criminal exchange of child pornography material on the Internet.
-The existing scientific material on this exchange lacks technical details that could help police detectives work more efficiently in child pornography cases.
-This research first takes a look at the existing literature on criminal child pornography exchange models.
-Thereafter it will look at the existing literature on new Internet based communication media, especially anonymization techniques.
-After this, a new criminal child pornography exchange model is presented and evaluated by interviewing police detectives concerned with online child pornography cases.
-The result of this research is a new criminal child pornography exchange model which allows for modeling anonymization within all the steps of the process.
+ABSTRACT
 \end{abstract}
 
-\keywords{child pornography, high tech crime, criminal exchange model}
+\begin{IEEEkeywords}
+Keywords
+\end{IEEEkeywords}
 
+\label{Introduction}
 \section{Introduction}
-With the arrest of Robert M.
-in December 2010\cite{site:bbc} the Netherlands' police agency caught, allegedly, the biggest child abuser ever in the Netherlands.
-On his computer detectives found (hidden in a partially deleted TrueCrypt folder) 8 terabyte containing images and videos of child abuse.
-Along with the images and videos came the digital equivalent of 64.000 A4 papers containing chat logs with other child abusers, which led to the arrest of numerous of other child abusers in the Netherlands, Norway, Germany, the United States, Australia and many more countries.
-These arrests led to the question whether current detection methods used by police agencies to catch child abusers are still valid for the new internet era \cite{wijk2009achter}.
-The current detection methods are based upon exchange models of child pornography (CP) which may not really be adapted to this new era and therefore they may need to be revised.
-This research will try to answer the question of how to revise such exchange models to satisfy the need of police detectives for better analysis and detection methods.
+Below is a list of 8 RFC assignments.
+Read and study the RFC (skip the very technical stuff such as ASN.1, focus on cryptographic and PKI matters).
+Then give a summary of the RFC on a high level, addressing the following issues:
+\begin{enumerate}
+	\item How does this RFC fit in the entire PKI picture? Who is expected to use this RFC,what for, and how?
+	\item What are the security requirements outlined in this RFC? What security problems does it attempt to solve? What (cryptographic) attacks does it defend against?
+	\item Give an overview of the solution that the RFC proposes. How is cryptography used in meeting the security requirements, solving the security problems, defending against the attacks?
+\end{enumerate}
+\bibliographystyle{IEEEtran}
+\bibliography{IEEEabrv,literature}
 
-Digital CP can be defined in multiple ways, this research will use a definition that is derived from the legal definition given by \cite{beech2008internet}, which cites the PROTECT Act of 2003:
-\begin{quote}
-	"...it is a crime to posses, manufacture or distribute pornography containing visual depictions of (a) a real child engaging in sexual acts or (b) a digital image, computer image, or computer generated image that is, or is indistinguishable from that of a minor engaged in sexually explicit conduct." from (18 U.S.
-Code Paragraph 2256(8) (B))
-\end{quote}
-This research acknowledges the legal definition of CP but it is not taking into account the issues related to computer generated images since they need to use different solutions than the ones discussed in the paper.
-Furthermore images and videos are widened to encompass digital material, leading to the following CP definition that is used by this research:
-\begin{quote} 
-	Digital child pornography is defined as digital pornography containing visual depictions of a real child engaging in sexual acts or a minor engaged in sexually explicit conduct. 
-\end{quote}
-
-To be able to describe the criminal process involved in the distribution, a type of model should be introduced to model the different steps involved in the process.
-This research will use Crime Schemes as proposed in \cite{willison2006understanding}.
-Steps in this process follow a flow.
-This means that certain processes depend on others, which need to be performed first.
-Groups of processes (categories) belong to each other and together form a category in the simplified model of the crime.
-In stealing a bike for example, there are different steps in how to break the lock, but they belong to each other and form the 'breaking the lock' category in the simplified model.
-Some different paths exist in breaking the lock, but it is always right to consider that one first needs to break the lock, before removing it from the bike.
-Since this research investigates exchange models and describe them via crime schemes, such an exchange model will from now on be called criminal exchange model.
-
-Different authors have suggested that there should be more scientific research into the area of criminal exchange models of CP \cite{wijk2009achter, wolak2005child, zee2007kinderpornografische}.
-They conclude that most of what is known about the exchange of CP is due to successful arrests and that there are exchange methods (involving high tech components) which are not yet found by police detectives.
-Therefore new research must be conducted to gather more information on these high tech crime components in the exchange of CP which could then be included in the existing criminal exchange models.
-
-The main research question in this research is 'How can the currently used main criminal exchange models of child pornography be adapted to describe (1) the current child pornography user behavior and (2) the new Internet based communication media used by child pornography offenders?'.
-This main research question is divided into four different subquestions:
-\begin{enumerate}
-	\item What are the currently used main criminal exchange models of CP?
-	\item What are the main differences between the communication media used in the past and today in the exchange of CP?
-	\item How can the changes associated with the current CP user behavior and the new internet based communication media be reflected in the currently used main criminal exchange models of CP? 
-\end{enumerate}
-
-The research questions (1) and (2) are answered using a literature study.
-Finally, research question (3) is answered by proposing a new CP criminal exchange model and by verifying it using interviews with police detectives that are concerned with the recent arrests of several child pornography offenders.
-
-This paper is organized as follows.
-In section 2 an overview of the current criminal exchange models of CP is given.
-Furthermore, this section provides the answer of the research question (1).
-Section 3 provides the technical enhancements on the CP criminal exchange models, providing the answer to research question (2).
-In Section 4 a new CP criminal exchange model is proposed that is verified by using interviews with police detectives that are concerned with the recent arrests of several child pornography offenders..
-Moreover, this section answers research question (3).
-Section 5 concludes and provides recommendations for future work.
-
-\section{Child Pornography Exchange Models}
-This section provides an overview of the current criminal CP exchange model. Furthermore, this section derives criteria and compares the discussed criminal CP exchange models.
-
-Several papers and books briefly mention the exchange of CP, such as \cite{wolak2005child, jenkins2001beyond, webb2007characteristics}, which briefly focus on CP exchange via Internet, \cite{quayle2002paedophiles, beech2008internet}, which briefly focus on the CP exchange via usenet, bulletin boards or websites.
-However, only few of these papers that describe the CP exchange, 	go into more detail, see e.g.
-\cite{en2011phishing,wortley2006child,wijk2009achter,callanan2009internet}.
-The description level of detail used by papers is quite different and will therefore be elaborated in different sections.
-
-However, only Faber et al.
-\cite{en2011phishing} provides a more complete description of a criminal CP exchange model.
-The other criminal CP exchange models discussed in this paper are derived by the author of this paper by carefully studying the information contained in the referenced papers and books.
-
-In Table \ref{tables:exchangeModelsCompared} the different criminal CP exchange models are compared. These CP exchange models are compared using the following criteria:
-
-\begin{itemize}
-	\item Completeness of the criminal exchange model: this refers to the number of categories modeled by the criminal exchange model. 
-		The steps defined in this research that need to be modeled by a criminal exchange model are:
-		\begin{itemize}
-			\item \textit{Production}: The physical abuse and the recording of it.
-Also location selection, victim recruiting, editing, lighting, restructuring of the video, etc.
-fall in this category since this research is not focused upon this category and only needs a way to model all processes that are not involved in the criminal exchange model.
-			\item \textit{Hiding}: Hiding information that could lead to the producer or distributor, by using techniques such as encryption and stenography \cite{krone2005international}.
-			\item \textit{Distribution}: Making CP material available for others to download/view.
-			\item \textit{Downloading}: Downloading or streaming CP material.
-			\item \textit{Storage}: Storing CP material and possibly hiding it.
-		\end{itemize}
-		In table \ref{tables:exchangeModelsCompared}, the grade ++ represents the situation that all the steps mentioned above are supported, while - - means that none of these steps are supported.
-	\item Modeling of Anonymity: this refers to whether the criminal exchange model, models in detail the support of anonymity in the criminal CP process.
-Anonymity support refers to support of activities in such a way that the identity of the CP user cannot be detected.
-In table \ref{tables:exchangeModelsCompared}, the grade ++ represents the situation that a criminal exchange model provides all means to model Anonymity support.
-The grade - - represents the situation that the criminal exchange model does not  provide any means of modeling Anonymity support.
-	\item Modeling of Distribution types: this refers to whether the criminal exchange model, models in detail the support of Distribution type in the CP process.
-Distribution type refers to the way of how the CP media is distributed.
-In table \ref{tables:exchangeModelsCompared}, the grade ++ represents the situation that a criminal exchange model provides all means to model the Distribution type.
-The grade - - represents the situation that the criminal exchange model does not provide any means of modeling the Distribution type.
-	\item Transaction type: this refers to the type of transactions involved within the Criminal CP process. These transactions can be either Financial means (money) or CP interchange material. 
-\end{itemize}
-
-\subsection{Faber et al., 2011 \cite{en2011phishing}}
-Figure \ref{fig:faber_01} gives the visual representation of the criminal CP exchange model proposed by \cite{en2011phishing}.
-This figure shows four different categories (\textit{Production},\textit{Hiding}, \textit{Distribution} and \textit{Storage}).
-\cite{en2011phishing} groups different steps in the process of the CP exchange.
-The step \textit{editing} is not included in such a group since it is not considered as being an important step in the criminal CP scheme.
-
-Faber et al.
-\cite{en2011phishing} is the only research document that describes some sort of criminal exchange model for the criminal process of CP.
-This criminal CP exchange model \cite{en2011phishing} describes the process that is sketched in Figure \ref{fig:faber_01}.
-The \textit{Editing} event is just a video editing event and therefore it can be left out of the exchange model.
-The different types of steps that could be taken in the \textit{Coding} event are similar to what other authors have concluded (i.e.
-\cite{wortley2006child, jenkins2001beyond,wolak2005child}).
-It includes untraceability, invisibility, illegibility and unrecognizability.
-The \textit{Payment} event does not only involve cash payments, but also includes interchange of CP material which is found in several other articles as well (i.e.
-\cite{wortley2006child,wijk2009achter,wolak2005child}).
-The \textit{Distribution} event only covers the describing of different communication media such as newsgroups \cite{site:usenet}, bulletin boards \cite{site:bulletin}, P2P \cite{site:p2p}, e-mail, IRC \cite{site:IRC}, FTP \cite{site:FTP} and websites, but lacks to clarify the specifics for CP exchange on those communication media or the amount of usage on these different communication media.
-The authors of \cite{en2011phishing} make a clear distinction between the exchange via a website (acquire domain, acquire hosting and distribution) and exchange via other media (acquire costumers, payment, distribution).
-This is in clear contrast with different other papers, \cite{wortley2006child,wijk2009achter,callanan2009internet}, that all state that using a website to distribute CP always includes a payment.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[scale = 0.65, trim = 20 620 0 10]{images/Faber.pdf}
-\caption{Part of the Crime Scheme as proposed by Faber et al. in \cite{en2011phishing}}
-\label{fig:faber_01}
-\end{figure}
-
-The \textit{abuse recording} step is thoroughly described, covering topics as the severity of the recordings \cite{quayle2002paedophiles}, but it also covers topics such as the victim selection, grooming, consolidation, staff recruitment and location selection.
-The \textit{editing} step involves the anonymization of the abuse, making scenes, compiling it, making descriptions, etc.
-The \textit{acquire domain} and \textit{hosting} involve the process of getting a website and domain name to spread the material.
-This can be bought online using (stolen) credit cards, web money or servers that could be hacked.
-The \textit{acquire costumers} event describes the process of getting customers to find the CP material, in addition to websites, it involves mass mailing and it provides adds on the normal porn websites or getting inside costumers from fora or networks.
-The \textit{payment} event could be either money (using (stolen) credit cards, web money, billing companies) or interchange of CP material.
-The \textit{distribution} process involves the uploading and downloading of the CP material via virtual communities, news groups, fora, p2p, e-mail, chat, FTP and websites.
-The \textit{storage} step involves storing the material and hiding it from authorities and other users of that computer or network.
-
-The processes modeled by Faber et al.
-involving the abuse and pre-abuse steps are in this research modeled to one process called \textit{abuse recording}, and therefore it is classified into the \textit{Production} category.
-The steps modeled in the process \textit{coding} are used to hide the producer's and distributor's identity and is therefore classified into the \textit{Hiding} category.
-The processes that cover the \textit{acquire costumers} steps and the steps of leading them to the CP material are grouped together with the actual distribution and payment processes to form the \textit{Distribution} category.
-The storage process modeled by Faber et al.
-is considered to be the \textit{Storage} category in this research.
-
-Faber et al.
-elaborates thoroughly on the criminal CP exchange model and therefore are rated with a + on the completeness of the criminal model.
-The model lacks on providing details on modeling the anonymity and the ability to model Anonymity is therefore rated with a -.
-The up-to-date distribution media also lack and is therefore rated with a -.
-The types of transactions involved are both money and the interchange of CP material, see Table \ref{tables:exchangeModelsCompared}.
-
-\subsection{Wortley et al., 2006 \cite{wortley2006child}}
-Figure \ref{fig:wortley_01} provides the visual representation of the criminal CP exchange model proposed in \cite{wortley2006child}.
-This figure shows three different groups of processes (\textit{Production}, \textit{Distribution} and \textit{Downloading}).
-Wortley et al.
-\cite{wortley2006child} emphasize that recent police activity on different open or semi-closed networks has led most CP users to change their communication means to more closed networks such as closed P2P networks, closed bulletin boards and closed chat rooms instead of websites, e-mail and newsgroups.
-Similar results are found in \cite{wijk2009achter, callanan2009internet}.
-Furthermore, Wortley et al.
-state that there are hardly any financial interactions involved within the process of distribution since almost all new material is produced by amateurs who do not seek financial gain in their child abuse.
-This resembles findings by other research activities (i.e., \cite{beech2008internet,wijk2009achter}) but it contradicts findings provided by, among others, the UN in 2006 (cited in \cite{wijk2009achter}).
-The UN stated that global CP exchange made about 6 billion dollar in 2005.
-Furthermore \cite{webb2007characteristics}, states that about 50\% of all CP users have paid to watch CP.
-The information provided by \cite{beech2008internet,wijk2009achter}, \cite{webb2007characteristics} show that there is a big market for CP exchange.
-Wortley et al., \cite{wortley2006child} lacks to provide the necessary details on the specifics on the different communication media for the CP exchange.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[scale = 0.65, trim = 20 720 0 25]{images/Wortley.pdf}
-\caption{Derived Crime Scheme from Wortley et al. in \cite{wortley2006child}}
-\label{fig:wortley_01}
-\end{figure}
-
-The \textit{production} process models the production of material, mostly made by amateurs but also covers professional recordings.
-The \textit{distribution} process describes in short the existence of pedophile rings or organized crime groups that interchange the CP material on different platforms like websites, e-mail, instant messages, newsgroups, bulletin boards, chat and p2p.
-The \textit{downloading} process describes the actual search for CP material by CP users.
-In \cite{wortley2006child} is stated that mass mailings and the ads on normal porn websites hardly exist anymore.
-
-The process described by Wortley et al.
-as the \textit{production} process is modeled as the \textit{Production} category.
-The \textit{distribution} process is modeled as the \textit{Distribution} category and the \textit{downloading} process is modeled as the \textit{Downloading} category.
-
-Wortley et al.
-do not elaborate thoroughly on the criminal CP exchange model, therefore the completeness of the criminal model is rated with a + / -.
-The modeling of Anonymity is not supported and therefore rated with a - -.
-The ability to model up-to-date distribution media is a little bit better and therefore rated with a -.
-The type of transactions involved is only the interchange of CP material, see Table \ref{tables:exchangeModelsCompared}.
-
-\subsection{Van Wijk et al., 2009 \cite{wijk2009achter}}
-Figure \ref{fig:wijk_01} depicts the visual representation of the criminal exchange model provided by \cite{wijk2009achter}.
-This figure shows four different groups of processes (\textit{Production}, \textit{Distribution}, \textit{Downloading} and \textit{Storage}).
-
-Van Wijk et al.
-\cite{wijk2009achter} describes four different types of distribution; commercial distribution (via mail delivery), commercial websites (pay by credit card or emoney), open networks (open IRC channels, open P2P networks, open bulletin boards) and closed networks (chat, e-mail, closed bulletin boards and closed P2P networks).
-Because of recent police activity against CP, more or less all distribution is in the last category, see \cite{wortley2006child, callanan2009internet}.
-Van Wijk et al.
-takes a closer look into the high tech components involved in the \textit{distribution} process.
-However, the focus is more on the CP downloaders instead of being on the CP distributors.
-Some of the mentioned high tech components involve (1) virtual hard drives to browse without leaving traces on the computer \cite{site:VHD}, (2) the use of disk encryption software to hide downloaded material on specific parts of the hard drive \cite{site:diskenc}, (3) the use of proxy servers as storage locations or to browse anonymously \cite{site:proxy} and (4) software to erase a hard drive.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[scale = 0.65, trim = 20 650 0 0]{images/VanWijk.pdf}
-\caption{Derived Crime Scheme from Van Wijk et al. in \cite{wijk2009achter}}
-\label{fig:wijk_01}
-\end{figure}
-
-The process described by Van Wijk et al.
-as \textit{production} is mentioned in the model, but no further information is given about this step.
-The \textit{distribution} step is different from earlier models and elaborates more on the different distribution media.
-The distribution is split in four different types of distribution.
-\begin{itemize}
-	\item Commercial distribution: uses post-order to order CP material online and receive it by post mail. 
-	\item Commercial websites: websites that run on servers mostly located in eastern European cities, which are distributing the CP material by selling it online.
-	\item Open networks: networks, which can be used to distribute CP material without requiring any password or security protection.
-Such open networks are: open P2P networks, open chat rooms and open bulletin boards.
-	\item Closed networks: networks that can be used to distribute CP material using the same media as the open networks, but which are closed by using password and security protection, such as encryption and decryption.
-\end{itemize}
-
-The \textit{production} process is modeled as the \textit{Production} category.
-The different distribution media are grouped together as the \textit{Distribution} category since all these distribution media types involve the characteristics of this category.
-The \textit{downloading} process is modeled as the \textit{Downloading} category and the \textit{storage} process is modeled as the \textit{Storage} category.
-
-Van Wijk et al.
-elaborates on the criminal exchange model and the completeness of the criminal model is therefore rated with a+.
-It also presents some details on the Anonymity support and that is therefore rated a +.
-The ability to model up-to-date distribution media is relatively extensive and therefore rated with a +.
-The types of transactions involved are encompassing both money and interchange of CP material, see Table \ref{tables:exchangeModelsCompared}.
-
-\subsection{Callanan et al., 2009 \cite{callanan2009internet}}
-Figure \ref{fig:callanan_01} depicts the visual representation of the criminal exchange model provided in \cite{callanan2009internet}.
-This figure shows two different groups of processes (\textit{Downloading} and \textit{Distribution}).
-
-Callanan et al.
-\cite{callanan2009internet} describes different communication media used to distribute CP material than the other CP exchange models described in the previous subsections.
-In particular, \cite{callanan2009internet} describes Freenet \cite{site:freenet} as a way to distribute CP material in encrypted and sliced packets which are then on a P2P manner distributed to users of Freenet (including non CP users).
-Freenet supports multiple anonymity options, making it possible to easily hide the identity of its users.
-Furthermore, \cite{callanan2009internet} describes several characteristics of Usenet system and the incentives of why this system is used among CP users.
-Both these communication media (i.e., \textit{distribution} process) have the characteristic that it is really hard to delete the CP material once it has been distributed.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[scale = 0.65, trim = 20 690 0 40]{images/Callanan.pdf}
-\caption{Derived Crime Scheme from Callanan et al. in \cite{callanan2009internet}}
-\label{fig:callanan_01}
-\end{figure}
-
-The hiding identity process describes different communication media that could be used either by downloaders of distributors for the exchange of CP.
-The actual downloading process models anonymity support by those communication media.
-The distribution process describes the anonymity support offered to distributors of CP material.
-
-\cite{callanan2009internet} describes various methods of identity hiding, which in turn could be used for downloading and/or distribution.
-The \textit{hiding} identity process describes different communication media that could be used by either CP material downloaders or CP material distributors.
-The actual \textit{downloading} process encompasses the anonymity support used by those communication media.
-The \textit{distribution} process encompasses the anonymity support offered to distributors of CP material.
-The \textit{hiding identity} process as modeled by Callanan et al.
-cannot be classified on any of the categories introduced at the introductory part of this section.
-In particular, this process encompasses both the identity hiding of CP material downloaders and CP material distributors.
-The \textit{downloading} process is modeled as the \textit{Downloading} category and the \textit{distribution} process is modeled as the \textit{Distribution} category.
-
-Callanan et al.
-does not elaborate on the criminal exchange model and the completeness of the criminal model is therefore rated a -.
-The detailed description of Anonymity support is rated with a + +.
-The detailed description of up-to-date distribution media is also rated with a + +, since it is very elaborative.
-The types of transactions involved are not discussed, see Table \ref{tables:exchangeModelsCompared}.
-
-\subsection{Conclusion}
-A comparison between the criminal CP exchange models described in this section is depicted in Table \ref{tables:exchangeModelsCompared}.
-The criteria used for this comparison are given in the introductory part of section 2.1.
-From this table it can be seen that the only detailed criminal CP exchange model is found in only \cite{en2011phishing}.
-The components by this model are also mentioned by other authors as well, except for the lack of payment in distribution via websites, which is not covered in \cite{en2011phishing}.
-The amount of usage of different communication media has made a switch from open networks to more closed ones as found by \cite{wortley2006child,wijk2009achter}.
-The types of CP payment methods mentioned in the exchange models differ.
-Though, it can be stated that the more advanced a CP user is, the less likely he/she will favorit paying for CP material.
-In particular, he/she will be far more interested in interchanging CP material, and thereby becoming more and more important in the online world of CP exchange \cite{wijk2009achter,quayle2002paedophiles,krone2005international,en2011phishing}.
-\cite{wijk2009achter} describes several high tech components involved in the CP material \textit{downloading} process and its \texttt{distribution} (virtual hard disks, disk encryption software and proxy servers).
-\cite{callanan2009internet} describes in more detail several communication media types (Usenet and Freenet) and the anonymity support used for the actual CP material distribution.
-However, \cite{callanan2009internet} is not providing any information on the used transaction types.
-\cite{en2011phishing} and \cite{wijk2009achter} use both Money and Interchange of CP material as transaction types, while \cite{wortley2006child} uses only the interchange of CP material as transaction type.
-
-\begin{table}[!ht]
-\caption{Comparison of current criminal CP exchange models}
-\begin{tabular}{|p{0.16\columnwidth}||p{0.15\columnwidth}|p{0.15\columnwidth}|p{0.15\columnwidth}|p{0.20\columnwidth}|}
-\hline
-\begin{sideways} \parbox{30mm}{\centering Author} \end{sideways} & \begin{sideways} \parbox{30mm}{\centering Completeness of the criminal exchange model} \end{sideways} & \begin{sideways} \parbox{30mm}{\centering Modeling of Anonymity} \end{sideways} &  \begin{sideways} \parbox{30mm}{\centering Modeling of Distribution types} \end{sideways} & \begin{sideways} \parbox{30mm}{\centering Transaction type} \end{sideways} \\ \hline & \\[-1em]\hline
-Faber et al. \cite{en2011phishing} & + & - & - & Money and interchange \\ \hline
-Wortley et al. \cite{wortley2006child} & +/- & - - & -  & Interchange \\ \hline
-Van Wijk et al. \cite{wijk2009achter}   & + & + & + & Money and interchange \\ \hline
-Callanan et al. \cite{callanan2009internet}   & - & + + & + + & Not discussed \\ \hline
-\end{tabular}
-\label{tables:exchangeModelsCompared}
-\end{table}
-
-\section{Enhancements of CP exchange model components}
-This section describes the ongoing technical enhancements on the CP criminal exchange models.
-The technical enhancements that will be discussed in this section will also be rated on the scale that the different criminal exchange models were rated on in section 2.
-The results can be found in Table \ref{tables:dataExchangeCompared}.
-
-\subsection{The Onion Routing (TOR)}
-Routing traffic through different hops is a method of anonymizing internet browsing and has been used for several years \cite{patil1963high}.
-In 2004, Dingledine et al.
-\cite{dingledine2004tor} proposed the so called The Onion Routing (TOR) protocol in which traffic is routed through three different hops and is encrypted in such a way that hops along the way can only see the identity of the previous hop as being the sender and the identity of the next hop as being the destination.
-In other words the intermediate hops cannot see the identity of the sender that created the packet and the identity of the receiver where the generated packet was addressed to.
-This provides in principle maximum anonymity since hop1 only knows the sender and hop2, hop2 only knows hop1 and hop3 and hop3 only knows hop2 and the final destination.
-None of the hops are able to know both the sender and the receiver of the internet traffic.
-Since the encryption standards and security protocols are verified \cite{goldberg2006security} to be secure if used properly, this could provide high anonymity for CP users.
-Furthermore, \textit{TOR} provides the so called 'hidden services'.
-Hidden services are websites that can only be accessed if their address is known (being a 16 character wide random address).
-The location of the hidden services remains a secret since accessing the address is provided through a rendezvous point.
-Connections from the rendezvous point to the sender or receiver are done through \textit{TOR} (and thus uses at least three hops).
-Visiting such hidden services is done by connecting to a rendezvous point through \textit{TOR} (meaning that the rendezvous does not know who the sender is), which than opens a connection to the hidden services through \textit{TOR} (meaning that hidden services doesn't know who the rendezvous point is).
-It could therefore be deduced that both the sender and the hidden service are not able to know the identity of the opponent.
-This also holds for the rendezvous point.
-This could stimulate CP users to upload and share CP material using hidden services that are specially designed for CP.
-In that way distributors and downloaders of CP are considered to be completely anonymous.
-
-\textit{TOR} is able to support various categories of the CP criminal exchange model, namely \textit{Hiding}, \textit{Distribution}, \textit{Downloading} and \textit{Storage}.
-This is rated with a + for the completeness of the criminal exchange model, see Table \ref{tables:dataExchangeCompared} since \textit{Production} step is not included in this model.
-The support of Anonymity and Distribution methods are both graded with a + +, since they can be well provided by the hidden services.
-
-\subsection{Freenet}
-\textit{Freenet} \cite{clarke2001freenet} provides similar features as the hidden services provided by \textit{TOR}.
-The exception is that everybody is partly able to share the hidden service.
-Freenet is a P2P-service which routes and disseminates requests, uploads and downloads among different users in chunks \cite{clarke2001freenet}.
-All chunks are requested through different hops and are therefore spread anonymously.
-All content is encrypted and chopped into chunks before spread through the network.
-Freenet can be used in either Darknet mode or Opennet mode, where networks are based upon friends only or on the entire user base, respectively.
-
-Freenet is able to model various categories of the CP criminal exchange model, namely \textit{Hiding}, \textit{Distribution} and \textit{Downloading}.
-Since rarely requested parts disappear in the network, the \textit{Storage} category does not apply to Freenet.
-This is rated with a + / - for the completeness of the criminal exchange model, see Table \ref{tables:dataExchangeCompared}.
-The Anonymity that can be modeled along with the Distribution methods offered provide both criteria's with a + +.
-
-\subsection{Anonymous remailers}
-Normal email traffic can be subject of investigation since the source address is exposed, leading to loss of anonymity.
-To regain this level of anonymity, anonymous remailers can be used, see e.g.
-\cite{danezis2003mixminion}.
-In general, they are used to forward an email to someone anonymously by stripping all identifiable information of the email leaving nothing but the bare text and the receiver.
-Some of these remailers offer additional features such as the ability of two-way communication by storing lists of senders and their email addresses (though, this is hazardous information that is being stored).
-Since this could still lead to the threat of being discovered by applying traffic analysis, Mixminion remailers can be used \cite{danezis2003mixminion}.
-This type of remailers take notion of the traffic analysis characteristics and use multi-hops to forward emails using e.g., delays and encryption.
-
-\textit{Anonymous remailers} is able to support the distribution of CP material and the recruitment of costumers for CP websites.
-Since these processes are only involved in the Distribution, this is graded with a - - for the completeness of the criminal exchange model.
-Different design techniques of these remailers offers different levels of anonymity; it is often not very clear who runs a remailer and if it has not yet been hacked.
-It therefore can only get a grade of + for the ability of modeling anonymity.
-The number of distribution methods is not increased with the introduction of anonymous remailers, though, one of them (email) has been extended, it is therefore rated as a - on the modeling of distribution, see Table \ref{tables:dataExchangeCompared}.
-
-\subsection{TrueCrypt}
-\textit{TrueCrypt} is an on-the-fly encryption tool that can be used to encrypt either parts or complete harddisks.
-\textit{TrueCrypt} uses very strong cryptographic principles \cite{miao2010research} by which it can provide strong privacy if strong keys are used.
-TrueCrypt can thus be used to encrypt parts of the harddisk containing CP material for storage.
-Furthermore, \textit{TrueCrypt} offers the option to use hidden volumes within such an encryption partition.
-It is very difficult to detect and prove the existence of such a hidden volume, and it therefore provides plausible deniability of that hidden volume.
-A CP user could for example reveal the body of an encrypted partition which contains somewhat sensitive information, creating the plausible deniability for a hidden volume within the encrypted partition.
-
-Since \textit{TrueCrypt} only gives the possibility to model \textit{Storage}, it is rated with a - - on completeness of the exchange model.
-The plausible deniability makes it possible to rate with a + + on the ability to model anonymity.
-\textit{TrueCrypt} does not provide any support for CP material distribution and therefore it is rated with a - - on the modeling of distribution, see Table \ref{tables:dataExchangeCompared}.
-
-\subsection{Anonymous credit cards}
-Paying for CP material has been declining according to some research results \cite{wortley2006child,wijk2009achter,beech2008internet} since police investigators have been investigating the flow of money to get a hold on downloaders of CP.
-Due to this fact, CP distributors who were in the business only for financial reasons have disappeared and the transaction type of exchange has been changed to interchange of CP material.
-
-\textit{Anonymous credit cards} can be used to perform a transaction that involves CP exchange anonymously.
-These credit cards can be bought using cash and can be used to perform payments online and offline.
-Furthermore, they can be used to perform transactions from other (anonymous) credit cards or stolen credit cards.
-This could be used to buy CP material online anonymously, without the possibility of tracing the transaction \cite{wall2007cybercrime}.
-Therefore, this can be considered as being a new burst for commercial CP material distributed from countries with a lack of legislation on CP \cite{kierkegaard2008cybering}.
-
-\textit{Anonymous credit cards} only enhances the \textit{Distribution} category and is therefore rated with a - - on the completeness of the exchange model, see Table \ref{tables:dataExchangeCompared}.
-The anonymity that could possibly be modeled with anonymous credit cards is quiet strong, though, these credit cards infer a few risks when used other than in the CP process.
-It is therefore rated with a + on the ability to model anonymity.
-Since distribution methods are not enhanced, but only the payment method, the ability to model distribution is rated with a - -.
-
-\subsection{Webcam hacking}
-There have been reports \cite{mishna2009ongoing,salomon2010examples} of viruses that can turn webcams on without that the user of the computer knowing.
-This could lead to serious problems within the \textit{Abuse recording} process, e.g.
-with grooming and consolidation being easier if children are confronted with secretly recorded images or videos.
-
-These \textit{Webcam hacks} only enhances the \textit{Production} category and are therefore rated with a - - on the completeness of the exchange model, see Table \ref{tables:dataExchangeCompared}.
-The anonymity that could possibly be modeled with \textit{Webcam hacks} is quiet strong, it is rated with a + on the modeling of Anonymity.
-The Distribution modeling is not supported by \textit{Webcam hacks} and is rated with a - -.
-
-\begin{table}[!ht]
-\caption{Comparison of enhanced exchange methods}
-\begin{tabular}{|p{0.19\columnwidth}||p{0.15\columnwidth}|p{0.15\columnwidth}|p{0.15\columnwidth}|p{0.17\columnwidth}|}
-\hline
-\begin{sideways} \parbox{30mm}{\centering Technique} \end{sideways} & \begin{sideways} \parbox{30mm}{\centering Completeness of the criminal exchange model} \end{sideways} & \begin{sideways} \parbox{30mm}{\centering Modeling of Anonymity} \end{sideways} &  \begin{sideways} \parbox{30mm}{\centering Modeling of Distribution types} \end{sideways} & \begin{sideways} \parbox{30mm}{\centering Transaction type} \end{sideways} \\ \hline & \\[-1em]\hline
-TOR \cite{dingledine2004tor} & + & + + & + + & Not discussed \\ \hline
-Freenet \cite{clarke2001freenet} & +/- & + + & + +  & Not discussed \\ \hline
-Anonymous remailers \cite{danezis2003mixminion} & - - & + & - & Not discussed \\ \hline
-TrueCrypt \cite{miao2010research}   & - - & + + & - - & Not discussed \\ \hline
-Anonymous credit cards \cite{wall2007cybercrime}   & - - & + & - - & Money \\ \hline
-Webcam hacks \cite{mishna2009ongoing,salomon2010examples}   & - - & + & - - & Not discussed \\ \hline
-\end{tabular}
-\label{tables:dataExchangeCompared}
-\end{table}
-
-\section{Proposed Exchange Model}
-This section proposes a new CP criminal exchange model (Section 4.1 and 4.2) that is verified by the use of interviews with police detectives that are concerned with the recent arrests of several child pornography offenders (Section 4.3).
-
-\subsection{Specification}
-A new criminal CP exchange model should be able to integrate most of the exchange models described in Sections 2 and 3. 
-Since the exchange model proposed by Faber et al. \cite{en2011phishing} provides the most complete criminal exchange model, it will be used as the main framework, see Figure \ref{fig:faber_01}.
-
-Some research results contradicted specific details of actions in the CP exchange model proposed by Faber et al.
-\cite{quayle2002paedophiles,krone2005international}.
-Furthermore, \cite{wijk2009achter} proposed to classify the distribution methods into four different categories of distribution.
-The \textit{Downloading} category was included in multiple CP exchange models (see Figures \ref{fig:callanan_01}, \ref{fig:wijk_01} and \ref{fig:wortley_01}) but was not present in Faber et al.'s model.
-These differences have been added to the original CP exchange model proposed by Faber et al., see Figure \ref{fig:newModel}.
-
-The step that is missing in the CP exchange model of Faber et al.
-and is strongly supported in other exchange models, e.g., in Callanan et al.
-\cite{callanan2009internet} TOR and Freenet, is related to Anonymity support.
-Therefore, the proposed exchange model will enhance the CP exchange model proposed by Faber et al.
-with the process \textit{Anonymity support}, see Figure \ref{fig:newModel}.
-As can be seen the \textit{Anonymity support} process impacts all other processes.
-This is due to the fact that Anonymity support can be applied on any of the CP exchange model processes proposed by Faber et al.
-In addition to this enhancement, each of the processes/steps encompassed in the enhanced CP exchange model should also include all possible known alternatives that can be used to realize the process. 
-Based on the information provided in Sections 2 and 3, we distinguish the following alternative solutions per each process of the enhanced CP exchange model.
-\subsubsection{Production}
-The possible alternative solutions that can be used to fulfill the \textit{Production} category and are described in Sections 2 and 3 are the following:
-\begin{itemize}
-	\item Abuse recording, see Section 2.1 and 3.6.\\
-		Abuse recording and the used solutions can be found in Faber et al.
-\cite{en2011phishing}.
-An additional solution that can be classified in the \textit{Abuse recording} process is the \textit{Webcam hacking} described in \cite{mishna2009ongoing,salomon2010examples}.
-\end{itemize}
-
-\subsubsection{Hiding}
-The possible alternative solutions that can be used to fulfill the \textit{Hiding} category and are described in Sections 2 and 3 are the following:
-\begin{itemize}
-	\item Coding, see Section 2.1.\\
-		Coding solutions can be found in Faber et al. \cite{en2011phishing}. The described features by Faber et al. are more elaborated in \cite{wortley2006child, jenkins2001beyond,wolak2005child}.
-		\begin{itemize}
-			\item \textit{Untraceability}: the disguise of the origin of the CP material. This mainly describes the deletion of metadata of a file.
-			\item \textit{Invisibility}: the disguise of CP material without the use of external software. This mainly describes the altering of file extensions and filenames.
-			\item \textit{Illegibility}: the encryption of CP material.
-			\item \textit{Unrecognizability}: the disguise of CP material with the use of external software. This mainly describes the stenography used to hide CP material inside other files and traffic.
-		\end{itemize}
-\end{itemize}
-
-\subsubsection{Distribution}
-The possible alternative solutions that can be used to fulfill the \textit{Distribution} category and are described in Sections 2 and 3 are the following:
-\begin{itemize}
-	\item Acquire domain and hosting, see Section 2.1\\
-		Acquire domain and hosting are described by Faber et al. \cite{en2011phishing}.
-	\item Acquire customers, see Section 2.1, 2.2, 2.3 and 3.3.\\
-		The acquiring of customers is described by Faber et al., Wortley et al., Van Wijk et al.
-\cite{en2011phishing, wortley2006child, wijk2009achter} and is enhanced by the use of \textit{Anonymous remailers} \cite{wall2007cybercrime}.
-	\item Payment, see Sections 2.1, 2.3, 3.1, 3.2 and 3.5.\\
-		Payment is originally described by Faber et al.
-\cite{en2011phishing} as financial transaction (money) and interchange of CP material, Van Wijk et al.
-In particular \cite{wijk2009achter} elaborates and motivates the use of payment and interchange of CP material.
-Both processes are enhanced by the use of \textit{TOR} \cite{dingledine2004tor}, \textit{Freenet} \cite{clarke2001freenet} and \textit{Anonymous credit cards} \cite{wall2007cybercrime}.
-	\item Distribution, see Sections 2.1, 2.2, 2.3, 2.4, 3.1, 3.2 and 3.3.\\
-		Distribution is roughly described by Faber et al., Wortley et al.
-and Van Wijk et al.
-\cite{en2011phishing,wortley2006child,wijk2009achter} and is more elaborated by Callanan et al.
-\cite{callanan2009internet}.
-This process is enhanced by the use of \textit{TOR} \cite{dingledine2004tor}, \textit{Freenet} \cite{clarke2001freenet} and \textit{Anonymous remailers} \cite{wall2007cybercrime}.
-\end{itemize}
-
-\subsubsection{Downloading}
-The possible alternative solutions	 that can be used to fulfill the \textit{Downloading} category and are described in Sections 2 and 3 are the following:
-\begin{itemize}
-	\item Downloading, see Sections 2.2, 2.3, 2.4, 3.1 and 3.2.\\
-		Downloading is only briefly mentioned by Wortley et al.
-\cite{wortley2006child}, Callanan et al.
-In particular, \cite{callanan2009internet} elaborate this process in more detail.
-Characteristics of downloaders are described by Van Wijk et al.\cite{wijk2009achter}.
-The enhancements introduced by \textit{TOR} \cite{dingledine2004tor} and \textit{Freenet} \cite{clarke2001freenet} can also be applied to this process.
-\end{itemize}
-
-\subsubsection{Storage}
-The possible alternative solutions that can be used to fulfill the \textit{Storage} category and are described in Sections 2 and 3 are the following:
-\begin{itemize}
-	\item Storage, see Sections 2.1, 2.3 and 3.4.\\
-		Storage is briefly described by Faber et al.
-\cite{en2011phishing}.
-Van Wijk et al.
-\cite{wijk2009achter} describes this process in more detail and introduces some aspects of \textit{physical storage}.
-\textit{TrueCrypt} \cite{miao2010research} enhances this process.
-\end{itemize}
-
-\subsubsection{Anonymity support}
-The possible alternative solutions that can be used to fulfill the ongoing \textit{Anonymity support} and are described in Sections 2 and 3 are the following:
-\begin{itemize}
-	\item Production
-		\begin{itemize}
-			\item Webcam hacks, see Section 3.6.\\
-				\textit{Webcam hacks} \cite{mishna2009ongoing,salomon2010examples} provides anonymity for producers of CP material.
-Producers can groom and consolidate children into recording CP material using their own webcam if they are confronted with secretly recorded material by the producer earlier.
-		\end{itemize}
-	\item Hiding
-		\begin{itemize}
-			\item Hiding identity, see Section 2.1.\\
-				\textit{Unrecognizability}, \textit{illegibility}, \textit{invisibility} and \textit{untraceability} of CP material provide additional anonymity for the producer of this CP material \cite{en2011phishing}.
-These techniques can be used to hide the identity of the producer before it gets distributed to a distributer.
-		\end{itemize}
-	\item Distribution
-		\begin{itemize}
-			\item \textit{Anonymous credit cards}, see Section 3.5.\\
-				\textit{Anonymous credit cards} \cite{wall2007cybercrime}: provides additional anonymity for distributers to register their domain and hosting. It also enhances the payment process.
-			\item \textit{Anonymous remailers}, see Section 3.3.\\
-				\textit{Anonymous remailers} \cite{wall2007cybercrime}: provides additional anonymity for distributers to acquire customers for their commercial CP website.
-			\item \textit{TOR}, see Section 3.1.\\
-				\textit{TOR} \cite{dingledine2004tor}: provides additional anonymity for costumers of commercial CP websites. It furthermore enhances the anonymity of other CP related internet surfing.
-			\item \textit{Hidden services} by \textit{TOR}, see Section 3.1.\\
-				\textit{TOR} \cite{dingledine2004tor}: provides additional anonymity for distributors of CP material.
-			\item \textit{Freenet} (Darknet mode), see Section 2.4 and 3.2.\\
-				\textit{Freenet} \cite{clarke2001freenet, callanan2009internet}: provides additional anonymity for distributors of CP material.
-		\end{itemize}
-	\item Downloading
-		\begin{itemize}
-			\item \textit{TOR}, see Section 3.1.\\
-				\textit{TOR} \cite{dingledine2004tor}: provides additional anonymity for downloaders / viewers of CP material.
-			\item \textit{Freenet} (Darknet mode), see Section 2.4 and 3.2.\\
-				\textit{Freenet} \cite{clarke2001freenet,callanan2009internet}: provides additional anonymity for downloaders of CP material.
-		\end{itemize}
-	\item Storage
-		\begin{itemize}
-			\item textit{Storage}, see Section 3.4.\\
-				\textit{TrueCrypt} \cite{miao2010research}: provides additional anonymity for the storage of CP material.
-		\end{itemize}
-\end{itemize}
-Several processes in the proposed criminal CP exchange model can be modeled in combination with the Anonymity support process, see Figure \ref{fig:newModel}.
-
-\subsection{Graphical representation}
-This section describes how the reader should interpret the graphical representation in Figure \ref{fig:newModel}.
-The graphical representation of the model is roughly built as an activity diagram as proposed by the UML standard \cite{eriksson2000business}.
-The process starts with the closed circle on the left going to the first category, namely \textit{Production}.
-Each arrow represents the closure of one step and the beginning of a new one (the start and the end of the arrow respectively).
-After the first few processes, there is a branch / choice (drawn as a black rectangle) after which there are three different methods of distribution.
-The post-order distribution is not included in this research.
-After the \textit{Distribution}, \textit{Downloading} and \textit{Storage} categories, the steps end in the closed circle with the open circle around it.
-
-\begin{figure*}[ht]
-\centering
-\includegraphics[scale = 0.8, trim = 0 530 0 0]{images/newModel.pdf}
-\caption{Proposed criminal CP exchange model}
-\label{fig:newModel}
-\end{figure*}
-
-\subsection{Verification}
-The verification of this newly proposed criminal CP exchange model is done by interviewing seven police detectives involved in the recent CP cases in the Netherlands.
-They belong to the Netherlands' police agency (govermental police agency).
-The detectives that have been interviewed have different backgrounds in CP or IT studies.
-
-In general the police detectives agree with the newly structured sequence of events in the criminal CP exchange process.
-They see it as a valuable addition to the earlier proposed exchange model by Faber et al.
-\ref{fig:faber_01} that the different distribution methods are split according to results by Van Wijk et al.
-\ref{fig:wijk_01}.
-The police detectives are not convinced that the \textit{Editing} process is not included in the \textit{Hiding} category.
-They argue that the \textit{Editing} process also involves the masking of the child abuser and therefore belongs to the \textit{Hiding} category.
-
-The results of the interview with the police detectives about the new proposed exchange model are analysed and given below:
-\begin{itemize}
-	\item \textit{Production}\\
-		\textit{Abuse recording}: The use of abuse recording step defined by Faber et al.
-\cite{en2011phishing} found by the detectives to be modeled satisfactorily enough in order to describe the \textit{Production} process.
-The enhancement described by the \textit{Webcam hacking} \cite{mishna2009ongoing,salomon2010examples} has not been observed by the interviewed police detectives in practice (i.e.
-during their daily work) yet.
-Though, colleague detectives from foreign countries have observed child abusers chatting about this option, but it is not certain whether it has really happened and used in practice.
-	\item \textit{Hiding}\\
-		\textit{Coding}: The mentioned techniques deduced from Faber et al.
-\cite{en2011phishing} \textit{untraceability}, \textit{invisibility}, \textit{illegibility} and \textit{unrecognizability} are partly recognized by the police detectives.
-In particular, they have observed several of cases in practice where the encryption (\textit{illegibility}) and deletion of metadata (\textit{untraceability} have been used.
-The use of external software (stenography in \textit{unrecognizability}) though, is hardly observed in practice.
-	\item \textit{Distribution}
-		\begin{itemize}
-			\item \textit{Acquire domain and hosting}: these processes are observed by police detectives in practice, though, only in foreign countries.
-Up to now, the police have not seen any cases in which Dutch CP users have registered Internet based domains and hosting to build a commercial CP website.
-The information deduced from Faber et al.
-\cite{en2011phishing} is found as being accurate, since the detectives have observed this activity also in practice.
-			\item \textit{Acquire customers}: as with the \textit{Acquire domain and hosting} processes, police detectives were only aware of foreign cases in which the active \textit{acquiring of customers} is observed.
-The use of \textit{Anonymous remailers} as suggested by the enhancements though, has not yet been observed in practice.
-			\item \textit{Payment}: as with the \textit{Acquire domain, hosting and customers} processes, police detectives were only aware of foreign cases in which the receiving of \textit{Payments} were processed.
-Though, there are cases in which Dutch CP users have paid to watch CP material on commercial websites and where in all of these cases, \textit{credit card payments} or different \textit{emoney payments} were made.
-The enhancement proposed by the \textit{Anonymous credit cards} have not been observed by the police detectives, in practice.
-The detectives do not expect to see this activity happening in the future in the Netherlands since buying such \textit{Credit Cards} in the Netherlands is really hard.
-			\item \textit{Distribution}: the distribution that is proposed by Faber et al., Wortley et al.
-and Van Wijk et al.
-\cite{en2011phishing, wortley2006child, wijk2009achter} are found by the detectives to be outdated.
-The new distribution methods are far more anonymized (e.g., Freenet \cite{clarke2001freenet} and TOR hidden services \cite{dingledine2004tor}).
-Therefore the proposed enhancements are found to be very valuable.
-Usenet, Fora, FTP, e-mail, etc.
-are not anymore being observed by police detectives in their daily police activities.
-		\end{itemize}
-	\item \textit{Downloading}\\
-		\textit{Downloading}: the police detectives emphasized that the most of the downloading takes place anonymously since the \textit{distribution} only prescribe downloading methods that are anonymous.
-Among them are browsing with the use of \textit{TOR} \cite{dingledine2004tor} and downloading CP material with the use of \textit{Freenet} \cite{clarke2001freenet}.
-The police detectives emphasized that the characteristics that are described by Van Wijk et al.
-\cite{wijk2009achter} give a valuable insight into the group of CP users.
-	\item \textit{Storage}\\
-		\textit{Storage}: the police detectives expected an elaborated description on the categorization obsession of CP material downloaders.
-The obsession is roughly described by Van Wijk et al.
-\cite{wijk2009achter} in the \textit{Downloading} process, but it could also be stretched/placed to the \textit{Storage} process, since it influences the way the storage of CP material is arranged.
-The enhancement of the \textit{Storage} process with the use of \textit{TrueCrypt} is sometimes observed in practice, but not often.
-\end{itemize}
-
-\section{Conclusions and Future Work}
-This paper focussed on how the currently used main criminal exchange models of child pornography can be adapted in order to describe (1) the current child pornography user behavior and (2) the new Internet based communication media used by child pornography offenders.
-Several research questions are derived and are answered by this paper.
-
-Section 2 answers research question (1), by describing four different criminal CP exchange models \cite{en2011phishing, wortley2006child, wijk2009achter, callanan2009internet}.
-Faber et al.
-\cite{en2011phishing} is the most elaborated model.
-
-Section 3 answers research question (2), by providing the technical enhancements on the CP criminal exchange models.
-In particular, six different enhancements to the existing CP exchange models were given, including \textit{The Onion Routing}, \textit{Freenet}, \textit{Anonymous remailers}, \textit{TrueCrypt}, \textit{Anonymous credit cards} and \textit{Webcam hacks}.
-
-Section 4 answers research question (3) by proposing a new criminal CP exchange model that is verified by using interviews with police detectives of the Netherlands' police agency that are concerned with the recent arrests of several child pornography offenders.
-The newly proposed CP exchange model has found its basis in the model proposed by Faber et al.
-\cite{en2011phishing} since this is the most elaborated one.
-
-The enhancements made to the model by Faber et al.
-include (1) process enhancements and (2) technical enhancements.
-The process enhancements make it clearer that there is a distinction between three different distribution techniques: commercial websites, post-order and open / closed networks.
-The technical enhancements model is related to the Anonymity support that is omitted in the model proposed by Faber et al.
-\cite{en2011phishing} and other researches.
-By analyzing these enhancements, including  the earlier proposed anonymization techniques, it could be deduced that \textit{Anonymity} impacts all processes available in the criminal CP exchange model.
-
-Future work includes three major research activities that could be undertaken.
-First of all, the list of enhancements proposed in Section 3 of this research is far from complete.
-They are found by the mere creativity of the author and could be researched more thoroughly (possibly including police detectives).
-The verification of the proposed model should be performed more thoroughly.
-This could be done using case studies based on real police cases, or by interviewing a higher number of police detectives, e.g.
-from local police agencies or from other countries.
-Finally, the effectiveness of this new proposed model should be measured in practice.
-
-\bibliographystyle{abbrv}
-\bibliography{paper}
-\vspace{50 mm}
-%APPENDICES are optional
-
-\balancecolumns
 \end{document}

### 2013-05-22 paper.tex
New paper!

--- 2013-05-22 paper.tex
@@
 % --- Author Metadata here --- DO NOT REMOVE OR CHANGE 
-\conferenceinfo{15$^{th}$ Twente Student Conference on IT}{June 21$^{st}$, 2012, Enschede, The Netherlands.}
+\conferenceinfo{17$^{th}$ Twente Student Conference on IT}{June 25$^{th}$, 2012, Enschede, The Netherlands.}
 \CopyrightYear{2012} % Allows default copyright year (200X) to be over-ridden - IF NEED BE.
@@
 
-\title{New exchange model for child pornography analysis [abstract V1 | sec1 V9 | sec2 V7 | sec3 V7 | sec4 V5 | sec5 V2]}
+\title{New Exchange Model for Child Pornography Analysis}
 
@@
 This research concentrates around the topic of the criminal exchange of child pornography material on the Internet.
-The existing scientific material on this exchange lacks technical details that could help police detectives work more efficiently in child pornography cases.
-This research first takes a look at the existing literature on criminal child pornography exchange models.
-Thereafter it will look at the existing literature on new Internet based communication media, especially anonymization techniques.
-After this, a new criminal child pornography exchange model is presented and evaluated by interviewing police detectives concerned with online child pornography cases.
-The result of this research is a new criminal child pornography exchange model which allows for modeling anonymization within all the steps of the process.
+The existing scientific material on this criminal exchange lacks technical details that could help police detectives work more efficiently in child pornography cases.
+This paper specifies a new criminal exchange model of child pornography that describes (1) the current child pornography user behavior and (2) the new Internet based communication media and anonymization techniques used by child pornography offenders.
+The specified criminal exchange model has been evaluated and verified by interviewing police detectives concerned with online child \\pornography cases.
 \end{abstract}
 
-\keywords{child pornography, high tech crime, criminal exchange model}
+\keywords{child pornography, high tech crime, criminal exchange\\ model}
 
@@
 With the arrest of Robert M.
-in December 2010\cite{site:bbc} the Netherlands' police agency caught, allegedly, the biggest child abuser ever in the Netherlands.
-On his computer detectives found (hidden in a partially deleted TrueCrypt folder) 8 terabyte containing images and videos of child abuse.
+in December 2010 \cite{site:bbc} the Netherlands' police agency caught, allegedly, the biggest child abuser ever in the Netherlands.
+On his computer, detectives found (hidden in a partially deleted TrueCrypt folder) eight terabyte containing images and videos of child abuse.
 Along with the images and videos came the digital equivalent of 64.000 A4 papers containing chat logs with other child abusers, which led to the arrest of numerous of other child abusers in the Netherlands, Norway, Germany, the United States, Australia and many more countries.
-These arrests led to the question whether current detection methods used by police agencies to catch child abusers are still valid for the new internet era \cite{wijk2009achter}.
+These arrests led to the question whether current detection methods used by police agencies to catch child abusers are still valid for the new Internet era \cite{wijk2009achter}.
 The current detection methods are based upon exchange models of child pornography (CP) which may not really be adapted to this new era and therefore they may need to be revised.
@@
 This research acknowledges the legal definition of CP but it is not taking into account the issues related to computer generated images since they need to use different solutions than the ones discussed in the paper.
-Furthermore images and videos are widened to encompass digital material, leading to the following CP definition that is used by this research:
+Furthermore, images and videos are widened to encompass digital material, leading to the following CP definition that is used by this research:
 \begin{quote} 
@@
 
-To be able to describe the criminal process involved in the distribution, a type of model should be introduced to model the different steps involved in the process.
+In order to be able to describe the criminal process involved in the distribution, a type of model should be introduced to model the different steps involved in the process.
 This research will use Crime Schemes as proposed in \cite{willison2006understanding}.
@@
 Groups of processes (categories) belong to each other and together form a category in the simplified model of the crime.
-In stealing a bike for example, there are different steps in how to break the lock, but they belong to each other and form the 'breaking the lock' category in the simplified model.
-Some different paths exist in breaking the lock, but it is always right to consider that one first needs to break the lock, before removing it from the bike.
-Since this research investigates exchange models and describe them via crime schemes, such an exchange model will from now on be called criminal exchange model.
+In stealing a bike for example, there are different steps in how to break the lock, but they relate to each other and form the 'breaking the lock' category in the simplified model.
+Some different paths exist in breaking the lock, but it is always right to consider that one needs to first break the lock, before removing it from the bike.
+Since this research investigates exchange models and describes them via crime schemes, such an exchange model will from now on be called a criminal exchange model.
 
@@
 
-The main research question in this research is 'How can the currently used main criminal exchange models of child pornography be adapted to describe (1) the current child pornography user behavior and (2) the new Internet based communication media used by child pornography offenders?'.
-This main research question is divided into four different subquestions:
+The main research question in this research is `How can the currently used main criminal exchange models of child pornography be adapted to describe (1) the current child pornography user behavior and (2) the new Internet based communication media and anonymization techniques used by child pornography offenders?'.
+This main research question is divided into three different sub questions:
 \begin{enumerate}
@@
 The research questions (1) and (2) are answered using a literature study.
-Finally, research question (3) is answered by proposing a new CP criminal exchange model and by verifying it using interviews with police detectives that are concerned with the recent arrests of several child pornography offenders.
+Finally, research question (3) is answered by proposing a new CP criminal exchange model and by verifying it using interviews with seven police detectives that are concerned with the recent arrests of several child pornography offenders.
 
 This paper is organized as follows.
-In section 2 an overview of the current criminal exchange models of CP is given.
+In Section 2 an overview of the current criminal exchange models of CP is given.
 Furthermore, this section provides the answer of the research question (1).
 Section 3 provides the technical enhancements on the CP criminal exchange models, providing the answer to research question (2).
-In Section 4 a new CP criminal exchange model is proposed that is verified by using interviews with police detectives that are concerned with the recent arrests of several child pornography offenders..
+In Section 4 a new CP criminal exchange model is proposed, which is verified by interviewing police detectives that are involved with the recent arrests of several child pornography offenders.
 Moreover, this section answers research question (3).
@@
 
-Several papers and books briefly mention the exchange of CP, such as \cite{wolak2005child, jenkins2001beyond, webb2007characteristics}, which briefly focus on CP exchange via Internet, \cite{quayle2002paedophiles, beech2008internet}, which briefly focus on the CP exchange via usenet, bulletin boards or websites.
+Several papers and books briefly mention the exchange of CP, such as \cite{wolak2005child, jenkins2001beyond, webb2007characteristics}, which briefly focus on CP exchange via Internet and, \cite{quayle2002paedophiles, beech2008internet}, which briefly focus on the CP exchange via usenet, bulletin boards or websites.
 However, only few of these papers that describe the CP exchange, 	go into more detail, see e.g.
@@
 	\item Completeness of the criminal exchange model: this refers to the number of categories modeled by the criminal exchange model. 
-		The steps defined in this research that need to be modeled by a criminal exchange model are:
+		The steps defined in this research, which need to be modeled by a criminal exchange model are:
 		\begin{itemize}
@@
 Also location selection, victim recruiting, editing, lighting, restructuring of the video, etc.
-fall in this category since this research is not focused upon this category and only needs a way to model all processes that are not involved in the criminal exchange model.
+fall in this category, since this research is not focused upon this category and only needs a way to model all processes that are not involved in the criminal exchange model.
 			\item \textit{Hiding}: Hiding information that could lead to the producer or distributor, by using techniques such as encryption and stenography \cite{krone2005international}.
@@
 		\end{itemize}
-		In table \ref{tables:exchangeModelsCompared}, the grade ++ represents the situation that all the steps mentioned above are supported, while - - means that none of these steps are supported.
+		In Table \ref{tables:exchangeModelsCompared}, the grade ++ represents the situation that all the steps mentioned above are supported, while - - means that none of these steps are supported.
 	\item Modeling of Anonymity: this refers to whether the criminal exchange model, models in detail the support of anonymity in the criminal CP process.
-Anonymity support refers to support of activities in such a way that the identity of the CP user cannot be detected.
-In table \ref{tables:exchangeModelsCompared}, the grade ++ represents the situation that a criminal exchange model provides all means to model Anonymity support.
+\\Anonymity support refers to the support of activities in such a way that the identity of the CP user cannot be detected.
+In Table \ref{tables:exchangeModelsCompared}, the grade ++ represents the situation that a criminal exchange model provides all means to model Anonymity support.
 The grade - - represents the situation that the criminal exchange model does not  provide any means of modeling Anonymity support.
@@
 Distribution type refers to the way of how the CP media is distributed.
-In table \ref{tables:exchangeModelsCompared}, the grade ++ represents the situation that a criminal exchange model provides all means to model the Distribution type.
+In Table \ref{tables:exchangeModelsCompared}, the grade ++ represents the situation that a criminal exchange model provides all means to model the Distribution type.
 The grade - - represents the situation that the criminal exchange model does not provide any means of modeling the Distribution type.
@@
 \cite{en2011phishing} groups different steps in the process of the CP exchange.
-The step \textit{editing} is not included in such a group since it is not considered as being an important step in the criminal CP scheme.
+The step \textit{Editing} is not included in such a group since it is not considered as being an important step in the criminal CP scheme.
 
@@
 It includes untraceability, invisibility, illegibility and unrecognizability.
-The \textit{Payment} event does not only involve cash payments, but also includes interchange of CP material which is found in several other articles as well (i.e.
+The \textit{Payment} event does not only involve cash payments, but also includes interchange of CP material that is found in several other articles as well (i.e.
 \cite{wortley2006child,wijk2009achter,wolak2005child}).
-The \textit{Distribution} event only covers the describing of different communication media such as newsgroups \cite{site:usenet}, bulletin boards \cite{site:bulletin}, P2P \cite{site:p2p}, e-mail, IRC \cite{site:IRC}, FTP \cite{site:FTP} and websites, but lacks to clarify the specifics for CP exchange on those communication media or the amount of usage on these different communication media.
+The \textit{Distribution} event only covers the description different communication media such as newsgroups \cite{site:usenet}, bulletin boards \cite{site:bulletin}, P2P \cite{site:p2p}, e-mail, IRC \cite{site:IRC}, FTP \cite{site:FTP} and websites, but lacks to clarify the specifics for CP exchange on those communication media or the amount of usage on these different communication media.
 The authors of \cite{en2011phishing} make a clear distinction between the exchange via a website (acquire domain, acquire hosting and distribution) and exchange via other media (acquire costumers, payment, distribution).
-This is in clear contrast with different other papers, \cite{wortley2006child,wijk2009achter,callanan2009internet}, that all state that using a website to distribute CP always includes a payment.
+This is in clear contrast with different other papers, \cite{wortley2006child,wijk2009achter,callanan2009internet}, which all state that using a website to distribute CP always includes a payment.
 
@@
 
-The \textit{abuse recording} step is thoroughly described, covering topics as the severity of the recordings \cite{quayle2002paedophiles}, but it also covers topics such as the victim selection, grooming, consolidation, staff recruitment and location selection.
-The \textit{editing} step involves the anonymization of the abuse, making scenes, compiling it, making descriptions, etc.
-The \textit{acquire domain} and \textit{hosting} involve the process of getting a website and domain name to spread the material.
+The \textit{Abuse Recording} step is thoroughly described, covering topics as the severity of the recordings \cite{quayle2002paedophiles}, but it also covers topics such as the victim selection, grooming, consolidation, staff recruitment and location selection.
+The \textit{Editing} step involves the anonymization of the abuse, making scenes, compiling it, making descriptions, etc.
+The \textit{Acquire Domain} and \textit{Hosting} involve the process of getting a website and domain name to spread the material.
 This can be bought online using (stolen) credit cards, web money or servers that could be hacked.
-The \textit{acquire costumers} event describes the process of getting customers to find the CP material, in addition to websites, it involves mass mailing and it provides adds on the normal porn websites or getting inside costumers from fora or networks.
-The \textit{payment} event could be either money (using (stolen) credit cards, web money, billing companies) or interchange of CP material.
-The \textit{distribution} process involves the uploading and downloading of the CP material via virtual communities, news groups, fora, p2p, e-mail, chat, FTP and websites.
-The \textit{storage} step involves storing the material and hiding it from authorities and other users of that computer or network.
+The \textit{Acquire Customers} event, describes the process of getting customers to find the CP material, in addition to websites, it involves mass mailing and it provides adds on the normal porn websites or getting inside costumers from fora or networks.
+The \textit{Payment} event could be either money (using (stolen) credit cards, web money, billing companies) or interchange of CP material.
+The \textit{Distribution} process involves the uploading and downloading of the CP material via virtual communities, news groups, fora, p2p, e-mail, chat, FTP and websites.
+The \textit{Storage} step involves storing the material and hiding it from authorities and other users of that computer or network.
 
 The processes modeled by Faber et al.
-involving the abuse and pre-abuse steps are in this research modeled to one process called \textit{abuse recording}, and therefore it is classified into the \textit{Production} category.
-The steps modeled in the process \textit{coding} are used to hide the producer's and distributor's identity and is therefore classified into the \textit{Hiding} category.
-The processes that cover the \textit{acquire costumers} steps and the steps of leading them to the CP material are grouped together with the actual distribution and payment processes to form the \textit{Distribution} category.
+involving the abuse and pre-abuse steps are in this research modeled to one process called \textit{Abuse Recording}, and therefore it is classified into the \textit{Production} category.
+The steps modeled in the process \textit{Coding} are used to hide the producer's and distributor's identity and is therefore classified into the \textit{Hiding} category.
+The processes that cover the \textit{Acquire Customers} steps and the steps of leading them to the CP material are grouped together with the actual distribution and payment processes to form the \textit{Distribution} category.
 The storage process modeled by Faber et al.
@@
 elaborates thoroughly on the criminal CP exchange model and therefore are rated with a + on the completeness of the criminal model.
-The model lacks on providing details on modeling the anonymity and the ability to model Anonymity is therefore rated with a -.
-The up-to-date distribution media also lack and is therefore rated with a -.
-The types of transactions involved are both money and the interchange of CP material, see Table \ref{tables:exchangeModelsCompared}.
+The model lacks on providing details on modeling the anonymity and the ability to model Anonymity Support is therefore rated with a -.
+Faber et al.
+also lacks on providing up-to-date distribution media and is therefore rated with a -.
+The types of transactions involved are both Money and the Interchange of CP material, see Table \ref{tables:exchangeModelsCompared}.
 
@@
 
-The \textit{production} process models the production of material, mostly made by amateurs but also covers professional recordings.
-The \textit{distribution} process describes in short the existence of pedophile rings or organized crime groups that interchange the CP material on different platforms like websites, e-mail, instant messages, newsgroups, bulletin boards, chat and p2p.
-The \textit{downloading} process describes the actual search for CP material by CP users.
-In \cite{wortley2006child} is stated that mass mailings and the ads on normal porn websites hardly exist anymore.
+The \textit{Production} process models the production of material, mostly made by amateurs but also covers professional recordings.
+The \textit{Distribution} process describes in short the existence of pedophile rings or organized crime groups that interchange the CP material on different platforms like websites, e-mail, instant messages, newsgroups, bulletin boards, chat and p2p.
+The \textit{Downloading} process describes the actual search for CP material by CP users.
+In \cite{wortley2006child}, it is stated that mass mailings and the ads on normal porn websites hardly exist anymore.
 
 The process described by Wortley et al.
-as the \textit{production} process is modeled as the \textit{Production} category.
-The \textit{distribution} process is modeled as the \textit{Distribution} category and the \textit{downloading} process is modeled as the \textit{Downloading} category.
+as the \textit{Production} process is modeled as the \textit{Production} category.
+The \textit{Distribution} process is modeled as the \textit{Distribution} category and the \textit{Downloading} process is modeled as the \textit{Downloading} category.
 
@@
 do not elaborate thoroughly on the criminal CP exchange model, therefore the completeness of the criminal model is rated with a + / -.
-The modeling of Anonymity is not supported and therefore rated with a - -.
+The modeling of Anonymity Support is not supported and therefore rated with a - -.
 The ability to model up-to-date distribution media is a little bit better and therefore rated with a -.
-The type of transactions involved is only the interchange of CP material, see Table \ref{tables:exchangeModelsCompared}.
+The type of transactions involved is only the Interchange of CP material, see Table \ref{tables:exchangeModelsCompared}.
 
@@
 \cite{wijk2009achter} describes four different types of distribution; commercial distribution (via mail delivery), commercial websites (pay by credit card or emoney), open networks (open IRC channels, open P2P networks, open bulletin boards) and closed networks (chat, e-mail, closed bulletin boards and closed P2P networks).
-Because of recent police activity against CP, more or less all distribution is in the last category, see \cite{wortley2006child, callanan2009internet}.
+Due to recent police activity against CP, more or less all distribution belongs to the last category, i.e.
+closed networks, see \cite{wortley2006child, callanan2009internet}.
 Van Wijk et al.
@@
 The process described by Van Wijk et al.
-as \textit{production} is mentioned in the model, but no further information is given about this step.
-The \textit{distribution} step is different from earlier models and elaborates more on the different distribution media.
+as \textit{Production} is mentioned in the model, but no further information is given about this step.
+The \textit{Distribution} step is different from earlier models and elaborates more on the different distribution media.
 The distribution is split in four different types of distribution.
@@
 
-The \textit{production} process is modeled as the \textit{Production} category.
+The \textit{Production} process is modeled as the \textit{Production} category.
 The different distribution media are grouped together as the \textit{Distribution} category since all these distribution media types involve the characteristics of this category.
-The \textit{downloading} process is modeled as the \textit{Downloading} category and the \textit{storage} process is modeled as the \textit{Storage} category.
+The \textit{Downloading} process is modeled as the \textit{Downloading} category and the \textit{Storage} process is modeled as the \textit{Storage} category.
 
 Van Wijk et al.
-elaborates on the criminal exchange model and the completeness of the criminal model is therefore rated with a+.
-It also presents some details on the Anonymity support and that is therefore rated a +.
+elaborates on the criminal exchange model and the completeness of the criminal model is therefore rated with a +.
+It also presents some details on the Anonymity support and therefore it is rated with a +.
 The ability to model up-to-date distribution media is relatively extensive and therefore rated with a +.
-The types of transactions involved are encompassing both money and interchange of CP material, see Table \ref{tables:exchangeModelsCompared}.
+The types of transactions involved are encompassing both Money and Interchange of CP material, see Table \ref{tables:exchangeModelsCompared}.
 
@@
 \cite{callanan2009internet} describes different communication media used to distribute CP material than the other CP exchange models described in the previous subsections.
-In particular, \cite{callanan2009internet} describes Freenet \cite{site:freenet} as a way to distribute CP material in encrypted and sliced packets which are then on a P2P manner distributed to users of Freenet (including non CP users).
-Freenet supports multiple anonymity options, making it possible to easily hide the identity of its users.
+In particular, \cite{callanan2009internet} describes Freenet \cite{site:freenet} as a way to distribute CP material in encrypted and sliced packets which are then distributed to users of Freenet on a P2P manner (including non CP users).
+Freenet supports multiple anonymization options, making it possible to easily hide the identity of its users.
 Furthermore, \cite{callanan2009internet} describes several characteristics of Usenet system and the incentives of why this system is used among CP users.
-Both these communication media (i.e., \textit{distribution} process) have the characteristic that it is really hard to delete the CP material once it has been distributed.
+Both these communication media (i.e., \textit{Distribution} process) have the characteristic that it is really hard to delete the CP material once it has been distributed.
 
@@
 
-The hiding identity process describes different communication media that could be used either by downloaders of distributors for the exchange of CP.
-The actual downloading process models anonymity support by those communication media.
-The distribution process describes the anonymity support offered to distributors of CP material.
+The \textit{Hiding Identity} process describes different communication media that could be used either by downloaders of distributors for the exchange of CP.
+The actual downloading process models Anonymity Support by those communication media.
+The distribution process describes the Anonymity Support offered to distributors of CP material.
 
 \cite{callanan2009internet} describes various methods of identity hiding, which in turn could be used for downloading and/or distribution.
-The \textit{hiding} identity process describes different communication media that could be used by either CP material downloaders or CP material distributors.
-The actual \textit{downloading} process encompasses the anonymity support used by those communication media.
-The \textit{distribution} process encompasses the anonymity support offered to distributors of CP material.
-The \textit{hiding identity} process as modeled by Callanan et al.
-cannot be classified on any of the categories introduced at the introductory part of this section.
+The \textit{Hiding} identity process describes different communication media that could be used by either CP material downloaders or CP material distributors.
+The actual \textit{Downloading} process encompasses the anonymity support used by those communication media.
+The \textit{Distribution} process encompasses the anonymity support offered to distributors of CP material.
+The \textit{Hiding Identity} process as modeled by Callanan et al.
+cannot be classified in any of the categories introduced at the introductory part of this section.
 In particular, this process encompasses both the identity hiding of CP material downloaders and CP material distributors.
-The \textit{downloading} process is modeled as the \textit{Downloading} category and the \textit{distribution} process is modeled as the \textit{Distribution} category.
+The \textit{Downloading} process is modeled as the \textit{Downloading} category and the \textit{Distribution} process is modeled as the \textit{Distribution} category.
 
 Callanan et al.
-does not elaborate on the criminal exchange model and the completeness of the criminal model is therefore rated a -.
+does not elaborate on the criminal exchange model and the completeness of the criminal model is therefore rated with a -.
 The detailed description of Anonymity support is rated with a + +.
@@
 The criteria used for this comparison are given in the introductory part of section 2.1.
-From this table it can be seen that the only detailed criminal CP exchange model is found in only \cite{en2011phishing}.
-The components by this model are also mentioned by other authors as well, except for the lack of payment in distribution via websites, which is not covered in \cite{en2011phishing}.
+From this table it can be seen that the only detailed criminal CP exchange model is found in \cite{en2011phishing}.
+The components of this model are mentioned by other authors as well, except for the lack of payment in distribution via websites, which is not covered in \cite{en2011phishing}.
 The amount of usage of different communication media has made a switch from open networks to more closed ones as found by \cite{wortley2006child,wijk2009achter}.
 The types of CP payment methods mentioned in the exchange models differ.
-Though, it can be stated that the more advanced a CP user is, the less likely he/she will favorit paying for CP material.
+Though, it can be stated that the more advanced a CP user is, the less likely he/she will favor paying for CP material.
 In particular, he/she will be far more interested in interchanging CP material, and thereby becoming more and more important in the online world of CP exchange \cite{wijk2009achter,quayle2002paedophiles,krone2005international,en2011phishing}.
-\cite{wijk2009achter} describes several high tech components involved in the CP material \textit{downloading} process and its \texttt{distribution} (virtual hard disks, disk encryption software and proxy servers).
+\cite{wijk2009achter} describes several high tech components involved in the CP material \textit{Downloading} process and its \textit{Distribution} (virtual hard disks, disk encryption software and proxy servers).
 \cite{callanan2009internet} describes in more detail several communication media types (Usenet and Freenet) and the anonymity support used for the actual CP material distribution.
@@
 This section describes the ongoing technical enhancements on the CP criminal exchange models.
-The technical enhancements that will be discussed in this section will also be rated on the scale that the different criminal exchange models were rated on in section 2.
+The technical enhancements that will be discussed in this section will also be rated on the scale that the different criminal exchange models were rated on in Section 2.
 The results can be found in Table \ref{tables:dataExchangeCompared}.
@@
 \subsection{The Onion Routing (TOR)}
-Routing traffic through different hops is a method of anonymizing internet browsing and has been used for several years \cite{patil1963high}.
+Routing traffic through different hops is a method of anony\-mizing internet browsing and has been used for several years \cite{patil1963high}.
 In 2004, Dingledine et al.
@@
 In other words the intermediate hops cannot see the identity of the sender that created the packet and the identity of the receiver where the generated packet was addressed to.
-This provides in principle maximum anonymity since hop1 only knows the sender and hop2, hop2 only knows hop1 and hop3 and hop3 only knows hop2 and the final destination.
+This provides in principle maximum anonymity since hop 1 only knows the sender and hop 2; hop 2 only knows hop 1 and hop 3; hop 3 only knows hop 2 and the final destination.
 None of the hops are able to know both the sender and the receiver of the internet traffic.
-Since the encryption standards and security protocols are verified \cite{goldberg2006security} to be secure if used properly, this could provide high anonymity for CP users.
-Furthermore, \textit{TOR} provides the so called 'hidden services'.
+Since the encryption standards and security protocols are verified \cite{goldberg2006security} to be secure, if used properly, could provide high anonymity for CP users.
+Furthermore, \textit{TOR} provides the so called `hidden services'.
 Hidden services are websites that can only be accessed if their address is known (being a 16 character wide random address).
@@
 Connections from the rendezvous point to the sender or receiver are done through \textit{TOR} (and thus uses at least three hops).
-Visiting such hidden services is done by connecting to a rendezvous point through \textit{TOR} (meaning that the rendezvous does not know who the sender is), which than opens a connection to the hidden services through \textit{TOR} (meaning that hidden services doesn't know who the rendezvous point is).
+Visiting such hidden services is done by connecting to a rendezvous point through \textit{TOR} (meaning that the rendezvous does not know who the sender is), which then opens a connection to the hidden services through \textit{TOR} (meaning that hidden services doesn't know who the rendezvous point is).
 It could therefore be deduced that both the sender and the hidden service are not able to know the identity of the opponent.
@@
 All chunks are requested through different hops and are therefore spread anonymously.
-All content is encrypted and chopped into chunks before spread through the network.
+The content is encrypted and chopped into chunks before spread through the network.
 Freenet can be used in either Darknet mode or Opennet mode, where networks are based upon friends only or on the entire user base, respectively.
 
-Freenet is able to model various categories of the CP criminal exchange model, namely \textit{Hiding}, \textit{Distribution} and \textit{Downloading}.
+Freenet is able to model various categories of the CP criminal exchange model, namely \textit{Hiding}, \textit{Distribution} and \\ \textit{Downloading}.
 Since rarely requested parts disappear in the network, the \textit{Storage} category does not apply to Freenet.
 This is rated with a + / - for the completeness of the criminal exchange model, see Table \ref{tables:dataExchangeCompared}.
-The Anonymity that can be modeled along with the Distribution methods offered provide both criteria's with a + +.
+The Anonymity Support and Distribution methods are well modeled.
+Therefore they are rated with a + +.
 
@@
 
-\textit{Anonymous remailers} is able to support the distribution of CP material and the recruitment of costumers for CP websites.
+\textit{Anonymous remailers} are able to support the distribution of CP material and the recruitment of costumers for CP websites.
 Since these processes are only involved in the Distribution, this is graded with a - - for the completeness of the criminal exchange model.
-Different design techniques of these remailers offers different levels of anonymity; it is often not very clear who runs a remailer and if it has not yet been hacked.
+Different design techniques of these remailers offer different levels of anonymity; it is often not very clear who runs a remailer and if it has not yet been hacked.
 It therefore can only get a grade of + for the ability of modeling anonymity.
-The number of distribution methods is not increased with the introduction of anonymous remailers, though, one of them (email) has been extended, it is therefore rated as a - on the modeling of distribution, see Table \ref{tables:dataExchangeCompared}.
+The number of distribution methods is not increased with the introduction of anonymous remailers, though, one of them (email) has been extended, it is therefore rated with a - on the modeling of distribution, see Table \ref{tables:dataExchangeCompared}.
 
@@
 \textit{TrueCrypt} uses very strong cryptographic principles \cite{miao2010research} by which it can provide strong privacy if strong keys are used.
-TrueCrypt can thus be used to encrypt parts of the harddisk containing CP material for storage.
-Furthermore, \textit{TrueCrypt} offers the option to use hidden volumes within such an encryption partition.
+\textit{TrueCrypt} can thus be used to encrypt parts of the harddisk containing CP material for storage.
+Furthermore, \textit{TrueCrypt} offers the option to use hidden volumes within such an encrypted partition.
 It is very difficult to detect and prove the existence of such a hidden volume, and it therefore provides plausible deniability of that hidden volume.
@@
 Since \textit{TrueCrypt} only gives the possibility to model \textit{Storage}, it is rated with a - - on completeness of the exchange model.
-The plausible deniability makes it possible to rate with a + + on the ability to model anonymity.
-\textit{TrueCrypt} does not provide any support for CP material distribution and therefore it is rated with a - - on the modeling of distribution, see Table \ref{tables:dataExchangeCompared}.
+The plausible deniability makes it possible to rate with a + + on the ability to model Anonymity Support.
+\textit{TrueCrypt} does not provide any support for CP material Distribution and therefore it is rated with a - - on the modeling of Distribution, see Table \ref{tables:dataExchangeCompared}.
 
@@
 This could be used to buy CP material online anonymously, without the possibility of tracing the transaction \cite{wall2007cybercrime}.
-Therefore, this can be considered as being a new burst for commercial CP material distributed from countries with a lack of legislation on CP \cite{kierkegaard2008cybering}.
+Therefore, this can potentially be considered as being a new burst for commercial CP material distributed from countries with a lack of legislation on CP \cite{kierkegaard2008cybering}.
 
 \textit{Anonymous credit cards} only enhances the \textit{Distribution} category and is therefore rated with a - - on the completeness of the exchange model, see Table \ref{tables:dataExchangeCompared}.
-The anonymity that could possibly be modeled with anonymous credit cards is quiet strong, though, these credit cards infer a few risks when used other than in the CP process.
-It is therefore rated with a + on the ability to model anonymity.
-Since distribution methods are not enhanced, but only the payment method, the ability to model distribution is rated with a - -.
+The anonymity that could possibly be modeled with anonymous credit cards is strong, though, these credit cards infer a few risks when used other than in the CP process.
+It is therefore rated with a + on the ability to model Anonymity Support.
+Since only the Payment method is enhanced and not the Distribution methods, the ability to model Distribution is rated with a - -.
 
@@
 This could lead to serious problems within the \textit{Abuse recording} process, e.g.
-with grooming and consolidation being easier if children are confronted with secretly recorded images or videos.
+with grooming and consolidation being easier if children are confronted with secretly\\ recorded images or videos.
 
 These \textit{Webcam hacks} only enhances the \textit{Production} category and are therefore rated with a - - on the completeness of the exchange model, see Table \ref{tables:dataExchangeCompared}.
-The anonymity that could possibly be modeled with \textit{Webcam hacks} is quiet strong, it is rated with a + on the modeling of Anonymity.
+The anonymity that could possibly be modeled with \textit{Webcam hacks} is strong and it is rated with a + on the modeling of Anonymity Support.
 The Distribution modeling is not supported by \textit{Webcam hacks} and is rated with a - -.
@@
 Furthermore, \cite{wijk2009achter} proposed to classify the distribution methods into four different categories of distribution.
-The \textit{Downloading} category was included in multiple CP exchange models (see Figures \ref{fig:callanan_01}, \ref{fig:wijk_01} and \ref{fig:wortley_01}) but was not present in Faber et al.'s model.
+The \textit{Downloading} category was included in multiple CP exchange models (see Figures \ref{fig:callanan_01}, \ref{fig:wijk_01} and \ref{fig:wortley_01}) but was not included in Faber et al.'s model.
 These differences have been added to the original CP exchange model proposed by Faber et al., see Figure \ref{fig:newModel}.
@@
 In addition to this enhancement, each of the processes/steps encompassed in the enhanced CP exchange model should also include all possible known alternatives that can be used to realize the process. 
-Based on the information provided in Sections 2 and 3, we distinguish the following alternative solutions per each process of the enhanced CP exchange model.
+Based on the information provided in Sections 2 and 3, we distinguish the following alternative solutions per each enhanced CP exchange model process.
 \subsubsection{Production}
@@
 	\item Acquire customers, see Section 2.1, 2.2, 2.3 and 3.3.\\
-		The acquiring of customers is described by Faber et al., Wortley et al., Van Wijk et al.
-\cite{en2011phishing, wortley2006child, wijk2009achter} and is enhanced by the use of \textit{Anonymous remailers} \cite{wall2007cybercrime}.
+		The acquiring of customers is described by Faber et al.
+\cite{en2011phishing}, Wortley et al.
+\cite{wortley2006child}, Van Wijk et al.
+\cite{wijk2009achter} and is enhanced by the use of \textit{Anonymous remailers} \cite{wall2007cybercrime}.
 	\item Payment, see Sections 2.1, 2.3, 3.1, 3.2 and 3.5.\\
@@
 	\item Distribution, see Sections 2.1, 2.2, 2.3, 2.4, 3.1, 3.2 and 3.3.\\
-		Distribution is roughly described by Faber et al., Wortley et al.
-and Van Wijk et al.
-\cite{en2011phishing,wortley2006child,wijk2009achter} and is more elaborated by Callanan et al.
+		Distribution is roughly described by Faber et al.
+\cite{en2011phishing}, Wortley et al.
+\cite{wortley2006child} and Van Wijk et al.
+\cite{wijk2009achter} and is more elaborated by Callanan et al.
 \cite{callanan2009internet}.
@@
 \cite{wortley2006child}, Callanan et al.
+\cite{callanan2009internet}.
 In particular, \cite{callanan2009internet} elaborate this process in more detail.
-Characteristics of downloaders are described by Van Wijk et al.\cite{wijk2009achter}.
+Characteristics of downloaders are described by Van Wijk et al.
+\cite{wijk2009achter}.
 The enhancements introduced by \textit{TOR} \cite{dingledine2004tor} and \textit{Freenet} \cite{clarke2001freenet} can also be applied to this process.
@@
 				\textit{Webcam hacks} \cite{mishna2009ongoing,salomon2010examples} provides anonymity for producers of CP material.
-Producers can groom and consolidate children into recording CP material using their own webcam if they are confronted with secretly recorded material by the producer earlier.
+Producers can groom and consolidate children into recording CP material using their own webcam if they are confronted with secretly earlier recorded material by the producer.
 		\end{itemize}
@@
 			\item \textit{Anonymous credit cards}, see Section 3.5.\\
-				\textit{Anonymous credit cards} \cite{wall2007cybercrime}: provides additional anonymity for distributers to register their domain and hosting. It also enhances the payment process.
+				\textit{Anonymous credit cards} \cite{wall2007cybercrime}: provides\\ additional anonymity for distributers to register their domain and hosting. It also enhances the payment process.
 			\item \textit{Anonymous remailers}, see Section 3.3.\\
@@
 				\textit{TOR} \cite{dingledine2004tor}: provides additional anonymity for downloaders / viewers of CP material.
-			\item \textit{Freenet} (Darknet mode), see Section 2.4 and 3.2.\\
+			\item \textit{Freenet} \cite{clarke2001freenet,callanan2009internet} (Darknet mode), see Section 2.4 and 3.2.\\
 				\textit{Freenet} \cite{clarke2001freenet,callanan2009internet}: provides additional anonymity for downloaders of CP material.
@@
 The graphical representation of the model is roughly built as an activity diagram as proposed by the UML standard \cite{eriksson2000business}.
-The process starts with the closed circle on the left going to the first category, namely \textit{Production}.
+The process starts with the closed circle on the left going to the first category, which is \textit{Production}.
 Each arrow represents the closure of one step and the beginning of a new one (the start and the end of the arrow respectively).
@@
 The verification of this newly proposed criminal CP exchange model is done by interviewing seven police detectives involved in the recent CP cases in the Netherlands.
-They belong to the Netherlands' police agency (govermental police agency).
+They belong to the Netherlands' police agency (governmental police agency).
 The detectives that have been interviewed have different backgrounds in CP or IT studies.
@@
 They see it as a valuable addition to the earlier proposed exchange model by Faber et al.
-\ref{fig:faber_01} that the different distribution methods are split according to results by Van Wijk et al.
-\ref{fig:wijk_01}.
-The police detectives are not convinced that the \textit{Editing} process is not included in the \textit{Hiding} category.
+(Figure \ref{fig:faber_01}) and where different \textit{Distribution} methods are split according to the results provided by Van Wijk et al.
+(Figure \ref{fig:wijk_01}).
+The police detectives are not convinced that the \textit{Editing} process should not be included in the \textit{Hiding} category.
 They argue that the \textit{Editing} process also involves the masking of the child abuser and therefore belongs to the \textit{Hiding} category.
 
-The results of the interview with the police detectives about the new proposed exchange model are analysed and given below:
+The results of the interview with the police detectives about the new proposed exchange model are analyzed and given below:
 \begin{itemize}
 	\item \textit{Production}\\
-		\textit{Abuse recording}: The use of abuse recording step defined by Faber et al.
-\cite{en2011phishing} found by the detectives to be modeled satisfactorily enough in order to describe the \textit{Production} process.
-The enhancement described by the \textit{Webcam hacking} \cite{mishna2009ongoing,salomon2010examples} has not been observed by the interviewed police detectives in practice (i.e.
+		\textit{Abuse recording}: The use of the \textit{Abuse Recording} step defined by Faber et al.
+\cite{en2011phishing} is found by the detectives to be modeled satisfactorily enough in order to describe the \textit{Production} process.
+The enhancement described by the \textit{Webcam hacking} \cite{mishna2009ongoing, salomon2010examples} has not been observed by the interviewed police detectives in practice (i.e.
 during their daily work) yet.
@@
 The enhancement proposed by the \textit{Anonymous credit cards} have not been observed by the police detectives, in practice.
-The detectives do not expect to see this activity happening in the future in the Netherlands since buying such \textit{Credit Cards} in the Netherlands is really hard.
-			\item \textit{Distribution}: the distribution that is proposed by Faber et al., Wortley et al.
-and Van Wijk et al.
-\cite{en2011phishing, wortley2006child, wijk2009achter} are found by the detectives to be outdated.
+The detectives do not expect to see this activity happening in the future in the Netherlands since buying such \\ \textit{Credit Cards} in the Netherlands is really hard.
+			\item \textit{Distribution}: the distribution that is proposed by Faber et al.
+\cite{en2011phishing}, Wortley et al.
+\cite{wortley2006child} and Van Wijk et al.
+\cite{wijk2009achter} are found by the detectives to be outdated.
 The new distribution methods are far more anonymized (e.g., Freenet \cite{clarke2001freenet} and TOR hidden services \cite{dingledine2004tor}).
@@
 	\item \textit{Downloading}\\
-		\textit{Downloading}: the police detectives emphasized that the most of the downloading takes place anonymously since the \textit{distribution} only prescribe downloading methods that are anonymous.
+		\textit{Downloading}: the police detectives emphasized that the most of the downloading takes place anonymously since the \textit{distribution} only prescribe downloading\\ methods that are anonymous.
 Among them are browsing with the use of \textit{TOR} \cite{dingledine2004tor} and downloading CP material with the use of \textit{Freenet} \cite{clarke2001freenet}.
@@
 \section{Conclusions and Future Work}
-This paper focussed on how the currently used main criminal exchange models of child pornography can be adapted in order to describe (1) the current child pornography user behavior and (2) the new Internet based communication media used by child pornography offenders.
+This paper focused on how the currently used main criminal exchange models of child pornography can be adapted in order to describe (1) the current child pornography user behavior and (2) the new Internet based communication media and anonymization techniques used by child pornography offenders.
 Several research questions are derived and are answered by this paper.
@@
 
-Section 4 answers research question (3) by proposing a new criminal CP exchange model that is verified by using interviews with police detectives of the Netherlands' police agency that are concerned with the recent arrests of several child pornography offenders.
+Section 4 answers research question (3) by proposing a new criminal CP exchange model that is verified by using interviews with seven police detectives of the Netherlands' police agency that are concerned with the recent arrests of several child pornography offenders.
 The newly proposed CP exchange model has found its basis in the model proposed by Faber et al.
@@
 First of all, the list of enhancements proposed in Section 3 of this research is far from complete.
-They are found by the mere creativity of the author and could be researched more thoroughly (possibly including police detectives).
+These enhancements are selected by the mere creativity of the author and could be researched more thoroughly (possibly including police detectives).
 The verification of the proposed model should be performed more thoroughly.

### 2013-05-22 paper.tex
work of day 1

--- 2013-05-22 paper.tex
@@
 
-\title{Internet Attribute Certificate Profile for Authorization - An Analyses}
-\author{Ruud Verbij}
-%begin document
+\title{Internet Attribute Certificate Profile for Authorization (RFC5755) - A Cryptographic Analyses}
+\author{Ruud Verbij \\ Student at the University of Twente \\ crypto@ruudverbij.nl}
 \begin{document}
@@
 \begin{IEEEkeywords}
-Keywords
+Attribute Certificate, Public Key Infrastructure, RFC5755, PKI, AC, Cryptography
 \end{IEEEkeywords}
@@
 \section{Introduction}
-Below is a list of 8 RFC assignments.
-Read and study the RFC (skip the very technical stuff such as ASN.1, focus on cryptographic and PKI matters).
-Then give a summary of the RFC on a high level, addressing the following issues:
-\begin{enumerate}
-	\item How does this RFC fit in the entire PKI picture? Who is expected to use this RFC,what for, and how?
-	\item What are the security requirements outlined in this RFC? What security problems does it attempt to solve? What (cryptographic) attacks does it defend against?
-	\item Give an overview of the solution that the RFC proposes. How is cryptography used in meeting the security requirements, solving the security problems, defending against the attacks?
-\end{enumerate}
+This paper outlines some of the cryptographic aspects offered by the Attribute Certificates\cite{rfc_ac} to the Public Key Infrastructure as defined by X.509\cite{rfc_x509}.
+Attribute Certificates (AC) is currently (may 2013) a \textit{Proposed Standard} with the IETF and is awaiting approval for the \textit{Draft Standard} category.
+The RFC5755 which covers AC's will obsolete an old IETF document describing AC's\cite{rfc_oldac}.
+
+The structure of this paper is as follows, Section~\ref{ac_in_pki} will introduce AC's.
+It covers the role of AC's within the entire PKI, the expected users and their usage of AC's.
+Section~\ref{cryptography_in_ac} describes what additional security features the use of AC brings and what role cryptography plays.
+Section~\ref{security_requirements} covers the security requirements involved when using AC's.
+
+This paper in no way presents a complete overview of the use of AC's within PKI.
+The reader is refered to \cite{rfc_ac} when working with, or having interest in the use of AC's within a PKI.
+The author is in no way responsible for any damage caused by this paper.
+The paper is written for Computer Science experts, especially those with interest in PKI and cryptography.
+This paper mainly consists of information from the RFC~\cite{rfc_ac}, except for statements which are followed by another reference.
+
+\label{ac_in_pki}
+\section{Attribute Certificates in the Public Key Infrastructure}
+How does this RFC fit in the entire PKI picture? Who is expected to use this RFC,what for, and how?
+\subsection{Introduction to AC}
+AC's are just like PKI certificates, except for the fact they lack a public key.
+This is due to the fact that AC's are not used for any cryptographic purposes.
+The main idea of an AC is to bind attributes to a PKI certificate (PKC) which cover topics like access control, data origin authentication, non-repudiation, etc.
+They typically belong to one or more PKCs, belong to can be read as \textit{signed by}, more on that in Section~\ref{cryptography_in_ac}.
+
+One may ask \textit{why} we need ACs when we already have PKC which tend to have more features (a public key).
+The use of ACs extends PKCs in the following way.
+It provides a \textit{temporary} set of attributes, binded to an identity (PKC) within an organisation.
+These attributes range from group identities, roles and clearance to charging identities and audit identities.
+It furthermore transfers the capabilities of granting access or authorization from the general PKC issuer within an organisation to special authorization authorities.
+
+ACs are typically used for granting this explicit \textit{temporary} access to a group or a role.
+This ensures a longer lifetime of the PKC binded to this AC.
+When the access or role for this individual for the service belonging to the AC is revoked or timed out, the AC is no longer valid, but the PKC can still be used.
+
+\subsection{Examples of usage}
+when used? --> auth, data origin auth, non-repudiation
+\subsection{Public Key Infrastructure to fit AC in}
+what does the infrastructure look? --> push and pull
+
+\label{cryptography_in_ac}
+\section{Cryptography in Attribute Certificates}
+Give an overview of the solution that the RFC proposes. How is cryptography used in meeting the security requirements, solving the security problems, defending against the attacks?
+--> what crypto is used how
+
+\label{security_requirements}
+\section{Security Requirements}
+What are the security requirements outlined in this RFC? What security problems does it attempt to solve? What (cryptographic) attacks does it defend against?
+
 \bibliographystyle{IEEEtran}
 \bibliography{IEEEabrv,literature}
-
 \end{document}

### 2013-05-22 paper.tex
Section II beta

@@
 
+\section{Introduction}
 \label{Introduction}
-\section{Introduction}
 This paper outlines some of the cryptographic aspects offered by the Attribute Certificates\cite{rfc_ac} to the Public Key Infrastructure as defined by X.509\cite{rfc_x509}.
@@
 
+\section{Attribute Certificates in the Public Key Infrastructure}
 \label{ac_in_pki}
-\section{Attribute Certificates in the Public Key Infrastructure}
-How does this RFC fit in the entire PKI picture? Who is expected to use this RFC,what for, and how?
+This section of the paper covers several topics, including an introduction to ACs, examples of usage and the Infrastructure necessary to work with  ACs.
+The purpose of this section is to describe the role of ACs in the entire picture of PKIs.
 \subsection{Introduction to AC}
-AC's are just like PKI certificates, except for the fact they lack a public key.
-This is due to the fact that AC's are not used for any cryptographic purposes.
-The main idea of an AC is to bind attributes to a PKI certificate (PKC) which cover topics like access control, data origin authentication, non-repudiation, etc.
-They typically belong to one or more PKCs, belong to can be read as \textit{signed by}, more on that in Section~\ref{cryptography_in_ac}.
+To begin with, AC's are just like PKI certificates, except for the fact they lack a public key.
+This is due to the fact that AC's are not used for any cryptographic purposes, but serve a different role.
+The main idea of an AC is to bind attributes to the identity of an individual through his/her PKI certificate (PKC).
+The attritbutes cover topics like access control, group identity, data origin authentication, non-repudiation, etc.
+They belong to one PKC in the sense that they are signed by a PKC, more on that in Section~\ref{cryptography_in_ac}.
 
-One may ask \textit{why} we need ACs when we already have PKC which tend to have more features (a public key).
-The use of ACs extends PKCs in the following way.
-It provides a \textit{temporary} set of attributes, binded to an identity (PKC) within an organisation.
+One may ask \textit{why} we need ACs when we already have PKC, which tend to have more features (a public key ie.).
+The introduction of ACs actually extends the usability of PKCs.
+This extention can be split into two different gains:
+\begin{itemize}
+	\item It provides for a \textit{temporary} set of attributes to be binded to an identity within an organisation.
 These attributes range from group identities, roles and clearance to charging identities and audit identities.
-It furthermore transfers the capabilities of granting access or authorization from the general PKC issuer within an organisation to special authorization authorities.
+	\item ACs allow for the transfer of granting access or authorization, from the general PKC issuer within an organisation to special authorization authorities.
+\end{itemize}
 
@@
 When the access or role for this individual for the service belonging to the AC is revoked or timed out, the AC is no longer valid, but the PKC can still be used.
+This is a major advantage to the use of PKCs for this purpose.
+It furthermore eases the general infrastructure of an organisation in the sense that the AC tells whether the binded identity (PKC) has access to this service instead of an online check for this access.
+AC' standard also offers the ability of AC revocation, more on that in Section~\ref{security_requirements}.
+
+The RFC~\cite{rfc_ac} compares PKCs to passports and ACs to Visa's.
+Passports tend to have a longer lifetime than Visa's, and the Visa's are binded to the identity of the owner by their passport.
+This analogy describes the use of ACs quite good, as Visa's also describe access control.
+But it lacks some of the extra features ACs offer, which will be described in the next subsection.
 
@@
 when used? --> auth, data origin auth, non-repudiation
+
 \subsection{Public Key Infrastructure to fit AC in}
@@
 
+\section{Cryptography in Attribute Certificates}
 \label{cryptography_in_ac}
-\section{Cryptography in Attribute Certificates}
 Give an overview of the solution that the RFC proposes. How is cryptography used in meeting the security requirements, solving the security problems, defending against the attacks?
@@
 
+\section{Security Requirements}
 \label{security_requirements}
-\section{Security Requirements}
 What are the security requirements outlined in this RFC? What security problems does it attempt to solve? What (cryptographic) attacks does it defend against?
+--> revocation
 

### 2013-05-29 paper.tex
Explained few example uses

@@
 \subsection{Examples of usage}
+An AC can be used in different security related services.
+"As an example it could also be used to certify authorization information related to a public key.
+More specifically, it may be used to limit the liability resulting from a digital signature, or to constrain the usage of a public key (e.g., transaction of a limited value, certain time windows, etc.)."~\cite{tilborg2011encyclopedia}.
+
+Different default attributes have been proposed, some of which are listed below.~\cite{benantar2006access,rfc_ac}
+\begin{itemize}
+	\item \textit{Service Authentication Information}, which identifies the AC holder to the service by name, with optional service-specific authentication information.
+This attribute could, by using some encryption scheme, also include the holder's identity and password.
+	\item \textit{Charging identity}, which is used to charge the holder for the use of services.
+	\item \textit{Role}, which is used to specify the role the holder has within a specific service.
+	\item \textit{Clearance}, which defines the clearance the holder has for specific information (secret, top-secret, etc.).
+	\item \textit{Group}, which describes the group the holder belongs to.
+\end{itemize}
+
 when used? --> auth, data origin auth, non-repudiation

### 2013-05-29 paper.tex
finalized the beta of exampels

@@
 The main idea of an AC is to bind attributes to the identity of an individual through his/her PKI certificate (PKC).
-The attritbutes cover topics like access control, group identity, data origin authentication, non-repudiation, etc.
+The attritbutes cover topics like access control, group identity, data origin authentication, etc.
 They belong to one PKC in the sense that they are signed by a PKC, more on that in Section~\ref{cryptography_in_ac}.
@@
 
-when used? --> auth, data origin auth, non-repudiation
+More rough examples~\cite{tilborg2011encyclopedia} indicate the use of ACs for DRM-secured devices. ACs could grant applications the right to install itself on devices like iPads and alike.
 

### 2013-05-29 paper.tex
Added diffs between AC and PKC

@@
 
+ Figure~\ref{fig:diff} shows the differences between an AC and a PKC.
+As can be seen, ACs hold a value referring to the holder.
+The RFC~\ref{rfc_ac} prescripes three ways in which such an AC can be bound to a PKC, of which only one may be used per AC.
+\begin{itemize}
+	\item \textit{baseCertificateID}, the issuer and serial number of the holder's PKC.
+"For any environment where the AC is passed in an authenticated message or session and where the authentication is based on the use of an X.509 PKC, the Holder field SHOULD use the baseCertificateID."~\cite{rfc_ac}
+	\item \textit{entityName}, the name of the claimant or role. This name must the same as on the PKC.
+	\item \textit{objectDigestInfo}, used to directly authenticate the holder. Which contains the certificate used itself.
+\end{itemize}
+Furthermore, it has a value containing the attributes belonging to this AC.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{diff.png}
+	\caption{Differences between PKC and AC~\cite{godavari2001secure}}
+	\label{fig:diff}
+\end{figure}
+
 \subsection{Examples of usage}
@@
 \subsection{Public Key Infrastructure to fit AC in}
-what does the infrastructure look? --> push and pull
+To use ACs within an organisation, there are mainly two implementation defaults, the so called \textit{push} and \textit{pull} models.
+This paper roughly describes the main arguments for choosing either of the two.
+
+The \textit{push} model requires the AC holder to own his AC.
+When speaking to the Server, he/she is required to attach the AC with the request.
+"The 'push' model is suitable in application where the client's permissions should be authenticated/validated in the client's 'home' domain."~\cite{godavari2001secure} This means that no new connections need to be set up between the Server and other parties, as will be in the \textit{pull} model.
+
+The \textit{pull} model requires the Server to retrieve the AC from a repository or an AC issuer.
+This means the implementation does not involve a change in the client-server protocol, which has benefit over the \textit{push} method when implemented within an existing infrastructure.
+"The 'pull' model is suitable when the client's priviliges should be authenticated in the inter-domain"~\cite{godavari2001secure} Furthermore, there is no need to update client's ACs when they expire, this can be done within the repository or AC issuer.
 
@@
 \label{cryptography_in_ac}
+This Section describes the role of cryptography within the use of ACs.
+
 Give an overview of the solution that the RFC proposes. How is cryptography used in meeting the security requirements, solving the security problems, defending against the attacks?

### 2013-05-29 paper.tex
fixed some bibs

@@
 As can be seen, ACs hold a value referring to the holder.
-The RFC~\ref{rfc_ac} prescripes three ways in which such an AC can be bound to a PKC, of which only one may be used per AC.
+The RFC~\cite{rfc_ac} prescripes three ways in which such an AC can be bound to a PKC, of which only one may be used per AC.
 \begin{itemize}
@@
 	\item \textit{entityName}, the name of the claimant or role. This name must the same as on the PKC.
-	\item \textit{objectDigestInfo}, used to directly authenticate the holder. Which contains the certificate used itself.
+	\item \textit{objectDigestInfo}, used to directly authenticate the holder. This objectDigestInfo contains a hash of an object the AC is linked to.
 \end{itemize}
@@
 \label{cryptography_in_ac}
-This Section describes the role of cryptography within the use of ACs.
+This Section describes the role of cryptography within the use of ACs and the way ACs are constructed and issued by an AC issuer.
+Lets stress again that this section is not ment to give a complete overview of the cryptography involved with ACs.
 
-Give an overview of the solution that the RFC proposes. How is cryptography used in meeting the security requirements, solving the security problems, defending against the attacks?
---> what crypto is used how
+\subsection{Issueing of an Attribute Certificate}
+Within an organisation, there must be a clear seperation between a Certificate Authority (CA) and an Attribute Certificate Authority (AA) as prescribed by the RFC~\cite{rfc_ac}.
+Within the same organisation the public key of the AA is distributed and trusted, which means that documents signed by the AA are trusted directly and not via a PKC path.
+An AA can build an AC and sign it using his private key, which can later on be verified by a Server or Service (AC verifier).
+
+After the AC has been build, either the \textit{push} or \textit{pull} model can be used to either distribute the AC to the client, or to distribute it to the AC repository.
+AC verifiers will verify the validity of an AC for an action or authenticate using the following steps.~\cite{rfc_ac}
+\begin{enumerate}
+	\item The AC holder's PKC must be present, and the entire certification path of that PKC must be verified.
+	\item The AC signature must be cryptographically correct and the issuers PKC certification path must be verified.
+	\item The AC issuer must be trusted directly (as mentioned above, the ACs Public Key should be trusted).
+	\item The time for which the AC is being evaluated must be within the AC validity.
+	\item The AC must follow the standard.
+	\item The AC must not contain unsupported critical extensions.
+	\item The AC should not have been revoked.
+\end{enumerate}
+
+\subsection{Cryptography}
+ACs are signed by the AA using a Signature Algorithm which is specified within the AC. The algorithms allowed for the signature are listed in different RFCs~\cite{rfc_alg1,rfc_alg2,rfc_alg3,rfc_alg4}.
 

### 2013-05-29 paper.tex
Version 1.0

@@
 \begin{abstract}
-ABSTRACT
+This paper touches upon some of the cryptographic and PKI elements concerned with Attribute Certificates.
+These attributes are used to extend the lifetime and functionality of regular Public Key Certificates in a Public Key Infrastructure.
+The Attribute Certificates are binded to a Public Key Certificate, have a shorter lifetime (quite temporarily) and add attributes from specific services to the Public Key Certificate.
+The attributes support all sorts of functionality, including authorization, access regulation, charging mechanisms and much more.
+This paper draws some of the characteristics and usage of Attribute Certificates in a Public Key Infrastructure, aswell as providing the reader with some security requirements when working with them.
 \end{abstract}
@@
 This paper outlines some of the cryptographic aspects offered by the Attribute Certificates\cite{rfc_ac} to the Public Key Infrastructure as defined by X.509\cite{rfc_x509}.
-Attribute Certificates (AC) is currently (may 2013) a \textit{Proposed Standard} with the IETF and is awaiting approval for the \textit{Draft Standard} category.
+Attribute Certificates (AC) is currently (may 2013) a \texttt{Proposed Standard} with the IETF and is awaiting approval for the \texttt{Draft Standard} category.
 The RFC5755 which covers AC's will obsolete an old IETF document describing AC's\cite{rfc_oldac}.
@@
 \begin{itemize}
-	\item \textit{baseCertificateID}, the issuer and serial number of the holder's PKC.
-"For any environment where the AC is passed in an authenticated message or session and where the authentication is based on the use of an X.509 PKC, the Holder field SHOULD use the baseCertificateID."~\cite{rfc_ac}
-	\item \textit{entityName}, the name of the claimant or role. This name must the same as on the PKC.
-	\item \textit{objectDigestInfo}, used to directly authenticate the holder. This objectDigestInfo contains a hash of an object the AC is linked to.
+	\item \texttt{baseCertificateID}, the issuer and serial number of the holder's PKC.
+\textit{"For any environment where the AC is passed in an authenticated message or session and where the authentication is based on the use of an X.509 PKC, the Holder field SHOULD use the baseCertificateID."}~\cite{rfc_ac}
+	\item \texttt{entityName}, the name of the claimant or role. This name must the same as on the PKC.
+	\item \texttt{objectDigestInfo}, used to directly authenticate the holder. This objectDigestInfo contains a hash of an object the AC is linked to.
 \end{itemize}
@@
 An AC can be used in different security related services.
-"As an example it could also be used to certify authorization information related to a public key.
-More specifically, it may be used to limit the liability resulting from a digital signature, or to constrain the usage of a public key (e.g., transaction of a limited value, certain time windows, etc.)."~\cite{tilborg2011encyclopedia}.
+\textit{"As an example it could also be used to certify authorization information related to a public key.
+More specifically, it may be used to limit the liability resulting from a digital signature, or to constrain the usage of a public key (e.g., transaction of a limited value, certain time windows, etc.)."}~\cite{tilborg2011encyclopedia}.
 
@@
 \begin{itemize}
-	\item \textit{Service Authentication Information}, which identifies the AC holder to the service by name, with optional service-specific authentication information.
+	\item \texttt{Service Authentication Information}, which identifies the AC holder to the service by name, with optional service-specific authentication information.
 This attribute could, by using some encryption scheme, also include the holder's identity and password.
-	\item \textit{Charging identity}, which is used to charge the holder for the use of services.
-	\item \textit{Role}, which is used to specify the role the holder has within a specific service.
-	\item \textit{Clearance}, which defines the clearance the holder has for specific information (secret, top-secret, etc.).
-	\item \textit{Group}, which describes the group the holder belongs to.
+	\item \texttt{Charging identity}, which is used to charge the holder for the use of services.
+	\item \texttt{Role}, which is used to specify the role the holder has within a specific service.
+	\item \texttt{Clearance}, which defines the clearance the holder has for specific information (secret, top-secret, etc.).
+	\item \texttt{Group}, which describes the group the holder belongs to.
 \end{itemize}
@@
 \subsection{Public Key Infrastructure to fit AC in}
-To use ACs within an organisation, there are mainly two implementation defaults, the so called \textit{push} and \textit{pull} models.
+To use ACs within an organisation, there are mainly two implementation defaults, the so called \texttt{push} and \texttt{pull} models.
 This paper roughly describes the main arguments for choosing either of the two.
 
-The \textit{push} model requires the AC holder to own his AC.
+The \texttt{push} model requires the AC holder to own his AC.
 When speaking to the Server, he/she is required to attach the AC with the request.
-"The 'push' model is suitable in application where the client's permissions should be authenticated/validated in the client's 'home' domain."~\cite{godavari2001secure} This means that no new connections need to be set up between the Server and other parties, as will be in the \textit{pull} model.
+\textit{"The 'push' model is suitable in application where the client's permissions should be authenticated/validated in the client's 'home' domain."}~\cite{godavari2001secure} This means that no new connections need to be set up between the Server and other parties, as will be in the \texttt{pull} model.
 
-The \textit{pull} model requires the Server to retrieve the AC from a repository or an AC issuer.
-This means the implementation does not involve a change in the client-server protocol, which has benefit over the \textit{push} method when implemented within an existing infrastructure.
-"The 'pull' model is suitable when the client's priviliges should be authenticated in the inter-domain"~\cite{godavari2001secure} Furthermore, there is no need to update client's ACs when they expire, this can be done within the repository or AC issuer.
+The \texttt{pull} model requires the Server to retrieve the AC from a repository or an AC issuer.
+This means the implementation does not involve a change in the client-server protocol, which has benefit over the \texttt{push} method when implemented within an existing infrastructure.
+\textit{"The 'pull' model is suitable when the client's priviliges should be authenticated in the inter-domain"}~\cite{godavari2001secure} Furthermore, there is no need to update client's ACs when they expire, this can be done within the repository or AC issuer.
+
+Figure~\ref{fig:PKI_models} shows the different protocol possibilities within one figure.
+It shows the different possible actors (AC issuer, Client or AC Holder, Server or AC verifier and Repository) and their possible communication flows.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{PKI_models.png}
+	\caption{Protocol communication for \textit{push} and \textit{pull} models~\cite{rfc_ac}}
+	\label{fig:PKI_models}
+\end{figure}
 
@@
 This Section describes the role of cryptography within the use of ACs and the way ACs are constructed and issued by an AC issuer.
-Lets stress again that this section is not ment to give a complete overview of the cryptography involved with ACs.
+Lets stress again that this paper is not ment to give a complete overview of the cryptography involved with ACs and the author is in no way responsible for any damage caused by the information in this paper.
 
@@
 
-After the AC has been build, either the \textit{push} or \textit{pull} model can be used to either distribute the AC to the client, or to distribute it to the AC repository.
-AC verifiers will verify the validity of an AC for an action or authenticate using the following steps.~\cite{rfc_ac}
+After the AC has been build, either the \texttt{push} or \texttt{pull} model can be used to either distribute the AC to the client, or to distribute it to the AC repository.
+AC verifiers will verify the validity of an AC for an action or authenticate using the following steps~\cite{rfc_ac}.
 \begin{enumerate}
@@
 	\item The AC must not contain unsupported critical extensions.
-	\item The AC should not have been revoked.
+	\item The AC should not have been revoked. (See Section~\ref{security_requirements})
 \end{enumerate}
@@
 \subsection{Cryptography}
-ACs are signed by the AA using a Signature Algorithm which is specified within the AC. The algorithms allowed for the signature are listed in different RFCs~\cite{rfc_alg1,rfc_alg2,rfc_alg3,rfc_alg4}.
+ACs are signed by the AA using a Signature Algorithm which is specified within the AC.
+The algorithms allowed for the signature are listed in different RFCs~\cite{rfc_alg1,rfc_alg2,rfc_alg3,rfc_alg4}.
+The RFC~\cite{rfc_ac} states \textit{"The binding between an AC holder and attributes cannot be stronger than the cryptographic module implementation and algorithms used to generate the signature.
+Short key lengths or weak hash algorithms will limit the utility of an AC.
+AC issuers are encouraged to note advances in cryptology so they can employ strong cryptographic techniques."} Which states clear that the responsibility for using cryptographic hash functions lies with the AA.
+
+The other cryptography that could be involved in ACs is the placement of login details (username and password) of an AC owner in the AC itself.
+In this case, ofcourse measures have to be taken to avoid plaintext passwords in the AC.
+The RFC~\cite{rfc_ac} let you decide upon proper cryptographic encryption functions necessary for the protection of the login credentials.
+The RFC~\cite{rfc_ac} suggests the use of Public Key Cryptography (encrypting with the Public Key of the Server or AC verifier).
+It is again the case that the AA is responsible for good cryptographic management of the issues mentioned previously.
 
@@
 \label{security_requirements}
-What are the security requirements outlined in this RFC? What security problems does it attempt to solve? What (cryptographic) attacks does it defend against?
---> revocation
+This section discusses the requirements set for the AC (which AC all meets) and discusses the security requirements necessary for securely operating with ACs.
+Furthermore it will touch upon AC revocation.
+
+\subsection{AC Requirements}
+The RFC~\cite{rfc_ac} enumerates a set of requirements they meet with this RFC.
+\begin{enumerate}
+	\item \textit{"Support for short-lived as well as long-lived ACs.
+Typical short-lived validity periods might be measured in hours, as opposed to months for PKCs.
+Short validity periods allow ACs to be useful without a revocation mechanism."} This is met by forceing the use of a validity value on an AC which can be set \texttt{YYYYMMDDHHMMSSZ}.
+	\item \textit{"Issuers of ACs should be able to define their own attribute types for use within closed domains."} This is met by allowing attributes to be made by the AAs themselves, though, keeping consistency by forceing the use of some predefined way of defining them.
+	\item \textit{"Some standard attribute types, which can be contained within ACs, should be defined.
+Examples include 'access identity', 'group', 'role', 'clearance', 'audit entity', and 'charging identity'"} This is met by having these implemented as defaults.
+	\item \textit{"Standard attribute types should be defined in a manner that permits an AC verifier to distinguish between uses of the same attribute in different domains.
+For example, the 'Administrators group' as defined by 'Baltimore' and the 'Administrator group' as defined by 'SPYRUS' should be easily distinguished."} This is met by allowing an optional \texttt{roleAuthority} for every \texttt{roleName}.
+	\item \textit{"It should be possible to 'target' an AC at one, or a small number of, servers.
+This means that a trustworthy non-target server will reject the AC for authorization decisions."} This is met by the implementation of so called \texttt{Target} and \texttt{TargetCert} fields.
+	\item \textit{"ACs should be defined so that they can either be 'pushed' by the client to the server, or 'pulled' by the server from a repository or other network service, including an online AC issuer."} This is met by the two possible implementation defaults for the Server or AC verifier.
+\end{enumerate}
+
+\subsection{Security Requirements for Safe Use}
+Several security requirements for safe use of ACs are recommended by the RFC~\cite{rfc_ac}.
+This subsection discusses most of them.
+For a complete view of the requirements, the reader is reffered to the RFC~\cite{rfc_ac}.
+
+\begin{itemize}
+	\item Masquerading of the AA after the private keys have been compromised could lead to serious security problems.
+The ACs that are created by an attacker are checked offline a Server or AC verifier, and therefore can cause serious damage.
+Revocation of the AAs public key (trust in the AA) should be performed to overcome this problems.
+Detection could be quite hard, since offline verification is done.
+This is especially dangerious if the \texttt{push} model is used, in which a rogue client can easily send his rogue AC to the AC verifier.
+
+	\item If an AA loses his private keys, this also leads to serious problems. All revocation lists have to be signed by the AA, and therefore, revocation becomes a critical problem.
+
+	\item AAs are recommended to have an online \texttt{AC Revocation Status Service} by which an AC verifier can easily check the status of an AC.
+The freshness of the AC Status highly reduces vulnerabilites since these are detected quicker.
+
+	\item Cryptographic hash functions, signing algorithms, public key cryptography, keylengths, etc.
+all are important since \textit{"The binding between an AC holder and attributes cannot be stronger than the cryptographic module implementation and algorithms used to generate the signature."}~\cite{rfc_ac}.
+
+	\item The RFC~\cite{rfc_ac} is really clear about how and what to check for the binding between the AC and the PKC.
+An AC verifier should strictly follow the protocol described by the RFC.
+Not following protocol, especially concering the fields for \texttt{entityName} and \texttt{baseCertificateID} could lead to serious security issues.
+
+	\item It is highly recommended to not use AC chains and to make the signing AA for an AC directly trustworthy.
+\end{itemize}
+
+\subsection{AC Revocation}
+This paper mentioned AC revocation several times, this Section will explain the rough base for AC revocation as set by the RFC~\cite{rfc_ac}.
+Typically, the use of ACs is ment \textit{temporarily}, and therefore revocation should occur less often than one sees within a PKC-like environment.
+Though, since situations (like some mentioned in the previous subsection) could occur in which revocation is desired, the AC standard allows for mechanisms to revoke ACs.
+Two mechanisms exist.
+
+The \texttt{Never revoke} scheme MUST be supported by all AC verifiers.
+This scheme lets ACs contain a possible \texttt{noRevAvail} field, which implicitly means that the status of the AC can be verified at the AA.
+This particular AC with the \texttt{noRevAvail} field set to true, will never end up on any revocation list and should therefore be checked at the AA.
+
+The \texttt{Pointer in AC} scheme allows for a \textit{pointer} to a revocation list or a source of revocation status information in the AC.
+The ACs that have fields set to use this scheme can end up at those lists.
+
+It is forbidden for an AC to be in both schemes.
+If an AC verifier only supports the \texttt{Never revoke} scheme, then all ACs who are using the \texttt{Pointer in AC} scheme must be rejected, since there status cannot be checked online (and the AC verifier does not support the revocation list pointers).
 

### 2013-05-29 paper.tex
Version 1.0 spell checked

@@
 This paper touches upon some of the cryptographic and PKI elements concerned with Attribute Certificates.
-These attributes are used to extend the lifetime and functionality of regular Public Key Certificates in a Public Key Infrastructure.
+These Attribute Certificates are used to extend the lifetime and functionality of regular Public Key Certificates in a Public Key Infrastructure.
 The Attribute Certificates are binded to a Public Key Certificate, have a shorter lifetime (quite temporarily) and add attributes from specific services to the Public Key Certificate.
@@
 Attribute Certificates (AC) is currently (may 2013) a \texttt{Proposed Standard} with the IETF and is awaiting approval for the \texttt{Draft Standard} category.
-The RFC5755 which covers AC's will obsolete an old IETF document describing AC's\cite{rfc_oldac}.
+The RFC5755 which covers AC's will obsolete an old IETF document describing ACs\cite{rfc_oldac}.
 
-The structure of this paper is as follows, Section~\ref{ac_in_pki} will introduce AC's.
-It covers the role of AC's within the entire PKI, the expected users and their usage of AC's.
+The structure of this paper is as follows, Section~\ref{ac_in_pki} will introduce ACs.
+It covers the role of ACs within the entire PKI, the expected users and their usage of ACs.
 Section~\ref{cryptography_in_ac} describes what additional security features the use of AC brings and what role cryptography plays.
-Section~\ref{security_requirements} covers the security requirements involved when using AC's.
+Section~\ref{security_requirements} covers the security requirements involved when using ACs.
 
-This paper in no way presents a complete overview of the use of AC's within PKI.
-The reader is refered to \cite{rfc_ac} when working with, or having interest in the use of AC's within a PKI.
+This paper in no way presents a complete overview of the use of ACs within PKI.
+The reader is referred to \cite{rfc_ac} when working with, or having interest in the use of ACs within a PKI.
 The author is in no way responsible for any damage caused by this paper.
@@
 \subsection{Introduction to AC}
-To begin with, AC's are just like PKI certificates, except for the fact they lack a public key.
-This is due to the fact that AC's are not used for any cryptographic purposes, but serve a different role.
+To begin with, ACs are just like PKI certificates, except for the fact that they lack a public key.
+This is due to the fact that ACs are not used for any cryptographic purposes, but serve a different role.
 The main idea of an AC is to bind attributes to the identity of an individual through his/her PKI certificate (PKC).
-The attritbutes cover topics like access control, group identity, data origin authentication, etc.
-They belong to one PKC in the sense that they are signed by a PKC, more on that in Section~\ref{cryptography_in_ac}.
+The attributes cover topics like access control, group identity, data origin authentication, etc.
+They belong to one PKC in the sense that they are mentioned in the AC, more on that in Section~\ref{cryptography_in_ac}.
 
@@
 These attributes range from group identities, roles and clearance to charging identities and audit identities.
-	\item ACs allow for the transfer of granting access or authorization, from the general PKC issuer within an organisation to special authorization authorities.
+	\item ACs allow for the transfer of granting access or authorization, from the general PKC issuer within an organisation to special authorization authorities (AA).
 \end{itemize}
@@
 
-Different default attributes have been proposed, some of which are listed below.~\cite{benantar2006access,rfc_ac}
+Different default attributes have been proposed, some of which are listed below~\cite{benantar2006access,rfc_ac}.
 \begin{itemize}
@@
 This means the implementation does not involve a change in the client-server protocol, which has benefit over the \texttt{push} method when implemented within an existing infrastructure.
-\textit{"The 'pull' model is suitable when the client's priviliges should be authenticated in the inter-domain"}~\cite{godavari2001secure} Furthermore, there is no need to update client's ACs when they expire, this can be done within the repository or AC issuer.
+\textit{"The 'pull' model is suitable when the client's priviliges should be authenticated in the inter-domain"}~\cite{godavari2001secure} Furthermore, there is no need to update client's ACs when they are renewed, this can be done within the repository or AC issuer.
 
@@
 Short key lengths or weak hash algorithms will limit the utility of an AC.
-AC issuers are encouraged to note advances in cryptology so they can employ strong cryptographic techniques."} Which states clear that the responsibility for using cryptographic hash functions lies with the AA.
+AC issuers are encouraged to note advances in cryptology so they can employ strong cryptographic techniques."} Which states clear that the responsibility for using proper Signing algorithms lies with the AA.
 
@@
 In this case, ofcourse measures have to be taken to avoid plaintext passwords in the AC.
-The RFC~\cite{rfc_ac} let you decide upon proper cryptographic encryption functions necessary for the protection of the login credentials.
+The RFC~\cite{rfc_ac} let the implementer decide upon proper cryptographic encryption functions necessary for the protection of the login credentials.
 The RFC~\cite{rfc_ac} suggests the use of Public Key Cryptography (encrypting with the Public Key of the Server or AC verifier).
@@
 This subsection discusses most of them.
-For a complete view of the requirements, the reader is reffered to the RFC~\cite{rfc_ac}.
+For a complete view of the requirements, the reader is referred to the RFC~\cite{rfc_ac}.
 
@@
 	\item Masquerading of the AA after the private keys have been compromised could lead to serious security problems.
-The ACs that are created by an attacker are checked offline a Server or AC verifier, and therefore can cause serious damage.
+The ACs that are created by an attacker are checked offline by a Server or AC verifier, and therefore can cause serious damage.
 Revocation of the AAs public key (trust in the AA) should be performed to overcome this problems.
-Detection could be quite hard, since offline verification is done.
+Detection could be quite hard, since offline verification is possible.
 This is especially dangerious if the \texttt{push} model is used, in which a rogue client can easily send his rogue AC to the AC verifier.
@@
 \subsection{AC Revocation}
-This paper mentioned AC revocation several times, this Section will explain the rough base for AC revocation as set by the RFC~\cite{rfc_ac}.
+This paper mentioned AC revocation several times, this subsection will explain the rough base for AC revocation as set by the RFC~\cite{rfc_ac}.
 Typically, the use of ACs is ment \textit{temporarily}, and therefore revocation should occur less often than one sees within a PKC-like environment.
